```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("auto_ml", "h2o")`

## Tuning Parameters

This model has no tuning parameters.

Engine arguments of interest 

- `max_runtime_secs` and `max_models`: controls the maximum running time and number of models to build in the automatic process. 

- `exclude_algos` and `include_algos`: a character vector indicating the excluded or included algorithms during model building. To see a full list of supported models, see the details section in [h2o::h2o.automl()].

- `validation`: An integer between 0 and 1 specifying the _proportion_ of training data reserved as validation set. This is used by h2o for performance assessment and potential early stopping. 

## Translation from parsnip to the original package (regression)

[agua::h2o_train_auto()] is a wrapper around [h2o::h2o.automl()]. 

```{r}
#| label: h2o-reg
auto_ml() |>  
  set_engine("h2o") |> 
  set_mode("regression") |> 
  translate()
```


## Translation from parsnip to the original package (classification)

```{r}
#| label: h2o-cls
auto_ml() |>  
  set_engine("h2o") |> 
  set_mode("classification") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Initializing h2o 

```{r}
#| child: template-h2o-init.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-bundle.Rmd
```
