```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("bag_mars", "earth")`

## Tuning Parameters

```{r earth-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("num_terms", "prod_degree", "prune_method"),
                 default = c("see below", "1L", "'backward'"))

param <-
  bag_mars() %>% 
  set_engine("earth") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r earth-param-list, echo = FALSE, results = "asis"}
param$item
```

The default value of `num_terms` depends on the number of predictor columns. For a data frame `x`, the default is `min(200, max(20, 2 * ncol(x))) + 1` (see [earth::earth()] and the reference below). 

## Translation from parsnip to the original package (regression)

```{r earth-reg}
bag_mars(num_terms = integer(1), prod_degree = integer(1), prune_method = character(1)) %>% 
  set_engine("earth") %>% 
  set_mode("regression") %>% 
  translate()
```

## Translation from parsnip to the original package (classification)

```{r earth-cls}
bag_mars(num_terms = integer(1), prod_degree = integer(1), prune_method = character(1)) %>% 
  set_engine("earth") %>% 
  set_mode("classification") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

## References

 - Breiman, L. 1996. "Bagging predictors". Machine Learning. 24 (2): 123-140
 
 - Friedman, J. 1991. "Multivariate Adaptive Regression Splines." _The Annals of Statistics_, vol. 19, no. 1, pp. 1-67.
 
 - Milborrow, S. ["Notes on the earth package."](http://www.milbo.org/doc/earth-notes.pdf) 
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

