```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("bag_mlp", "nnet")`

## Tuning Parameters

```{r nnet-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "hidden_units"),
                 default = c("0.0", "10L"))

param <-
 bag_mlp() %>% 
  set_engine("nnet") %>% 
  set_mode("regression") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r nnet-param-list, echo = FALSE, results = "asis"}
param$item
```

These defaults are set by the `baguette` package and are different than those in [nnet::nnet()]. 

## Translation from parsnip to the original package (classification)

`r uses_extension("bag_mlp", "nnet", "classification")`

```{r nnet-cls}
library(baguette)

bag_mlp(penalty = double(1), hidden_units = integer(1)) %>% 
  set_engine("nnet") %>% 
  set_mode("classification") %>% 
  translate()
```


## Translation from parsnip to the original package (regression)

`r uses_extension("bag_mlp", "nnet", "regression")`

```{r nnet-reg}
library(baguette)

bag_mlp(penalty = double(1), hidden_units = integer(1)) %>% 
  set_engine("nnet") %>% 
  set_mode("regression") %>% 
  translate()
```


## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

## Case weights

```{r child = "template-no-case-weights.Rmd"}
```


## References

 - Breiman L. 1996. "Bagging predictors". Machine Learning. 24 (2): 123-140

 - Kuhn, M, and K Johnson. 2013. *Applied Predictive Modeling*. Springer.
