```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("bag_tree", "rpart")`

## Tuning Parameters

```{r}
#| label: rpart-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "min_n", "cost_complexity", "class_cost"),
                 default = c("30L", "2L", "0.01", "(see below)"))

param <-
 bag_tree() |> 
  set_engine("rpart") |> 
  set_mode("regression") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: rpart-param-list
#| echo: false
#| results: asis
param$item
```

For the `class_cost` parameter, the value can be a non-negative scalar for a class cost (where a cost of 1 means no extra cost). This is useful for when the first level of the outcome factor is the minority class. If this is not the case, values between zero and one can be used to bias to the second level of the factor.


## Translation from parsnip to the original package (classification)

`r uses_extension("bag_tree", "rpart", "classification")`

```{r}
#| label: rpart-cls
library(baguette)

bag_tree(tree_depth = integer(1), min_n = integer(1), cost_complexity = double(1)) |> 
  set_engine("rpart") |> 
  set_mode("classification") |> 
  translate()
```


## Translation from parsnip to the original package (regression)

`r uses_extension("bag_tree", "rpart", "regression")`

```{r}
#| label: rpart-reg
library(baguette)

bag_tree(tree_depth = integer(1), min_n = integer(1), cost_complexity = double(1)) |> 
  set_engine("rpart") |> 
  set_mode("regression") |> 
  translate()
```

## Translation from parsnip to the original package (censored regression)

`r uses_extension("bag_tree", "rpart", "censored regression")`

```{r}
#| label: rpart-creg
library(censored)

bag_tree(tree_depth = integer(1), min_n = integer(1), cost_complexity = double(1)) |> 
  set_engine("rpart") |> 
  set_mode("censored regression") |> 
  translate()
```


## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Other details

```{r}
#| child: template-survival-median.Rmd
```

## References

 - Breiman L. 1996. "Bagging predictors". Machine Learning. 24 (2): 123-140
 
 - Hothorn T, Lausen B, Benner A, Radespiel-Troeger M. 2004. Bagging Survival Trees. _Statistics in Medicine_, 23(1), 77–91.
 
 - Kuhn, M, and K Johnson. 2013. *Applied Predictive Modeling*. Springer.
