# Engine Details

Engines may have pre-set default arguments when executing the model fit call. For this type of model, the template of the fit calls are below:

## xgboost

```{r xgboost-reg}
boost_tree() %>% 
  set_engine("xgboost") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r xgboost-csl}
boost_tree() %>% 
  set_engine("xgboost") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that, for most engines to `boost_tree()`, the `sample_size` argument is in terms of the _number_ of training set points. The `xgboost` package parameterizes this as the  _proportion_ of training set samples instead. When using the `tune`, this **occurs automatically**. 

If you would like to use a custom range when tuning `sample_size`, the `dials::sample_prop()` function can be used in that case. For example, using a  parameter set: 

```{r xgb-update, eval = FALSE}
mod <- 
  boost_tree(sample_size = tune()) %>% 
  set_engine("xgboost") %>% 
  set_mode("classification")

# update the parameters using the `dials` function
mod_param <- 
  mod %>% 
  parameters() %>% 
  update(sample_size = sample_prop(c(0.4, 0.9)))
```

Finally, note that `xgboost` models require that non-numeric predictors (e.g., factors) must be converted to dummy variables or some other numeric representation. 


## C5.0

```{r C5.0-csl}
boost_tree() %>% 
  set_engine("C5.0") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [C50::C5.0()] does not require factor predictors to be converted 
to indicator variables. 

## spark

```{r spark-reg}
boost_tree() %>% 
  set_engine("spark") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r spark-csl}
boost_tree() %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original names in each engine that has main parameters:

```{r echo = FALSE, results = "asis"}
parsnip::convert_args("boost_tree")
```

