```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("boost_tree", "spark")`. However, multiclass classification is not supported yet.

## Tuning Parameters

```{r}
#| label: spark-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "trees", "learn_rate", "mtry", "min_n", "loss_reduction", "sample_size"),
                 default = c("5L", "20L", "0.1", "see below", "1L", "0.0", "1.0"))

# For this model, this is the same for all modes
param <-
 boost_tree() |> 
  set_engine("spark") |> 
  set_mode("regression") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: spark-param-list
#| echo: false
#| results: asis
param$item
```

The `mtry` parameter is related to the number of predictors. The default depends on the model mode. For classification, the square root of the number of predictors is used and for regression, one third of the predictors are sampled. 

## Translation from parsnip to the original package (regression)

```{r}
#| label: spark-reg
boost_tree(
  mtry = integer(), trees = integer(), min_n = integer(), tree_depth = integer(),
  learn_rate = numeric(), loss_reduction = numeric(), sample_size = numeric()
) |>
  set_engine("spark") |>
  set_mode("regression") |>
  translate()
```

## Translation from parsnip to the original package (classification)

```{r}
#| label: spark-cls
boost_tree(
  mtry = integer(), trees = integer(), min_n = integer(), tree_depth = integer(),
  learn_rate = numeric(), loss_reduction = numeric(), sample_size = numeric()
) |> 
  set_engine("spark") |> 
  set_mode("classification") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

Note that, for spark engines, the `case_weight` argument value should be a character string to specify the column with the numeric case weights. 

## Other details

```{r}
#| child: template-spark-notes.Rmd
```

## References

 - Luraschi, J, K Kuo, and E Ruiz. 2019. _Mastering Spark with R_. O'Reilly Media

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

