```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("boost_tree", "spark")`. However, multiclass classification is not supported yet.

## Tuning Parameters

```{r spark-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "trees", "learn_rate", "mtry", "min_n", "loss_reduction", "sample_size"),
                 default = c("5L", "20L", "0.1", "see below", "1L", "0.0", "1.0"))

# For this model, this is the same for all modes
param <-
 boost_tree() %>% 
  set_engine("spark") %>% 
  set_mode("regression") %>% 
  tunable() %>% 
  dplyr::filter(name != "stop_iter") %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameters:

```{r spark-param-list, echo = FALSE, results = "asis"}
param$item
```

The `mtry` parameter is related to the number of predictors. The default depends on the model mode. For classification, the square root of the number of predictors is used and for regression, one third of the predictors are sampled. 

## Translation from parsnip to the original package (regression)

```{r spark-reg}
boost_tree(
  mtry = integer(), trees = integer(), min_n = integer(), tree_depth = integer(),
  learn_rate = numeric(), loss_reduction = numeric(), sample_size = numeric()
) %>%
  set_engine("spark") %>%
  set_mode("regression") %>%
  translate()
```

## Translation from parsnip to the original package (classification)

```{r spark-cls}
boost_tree(
  mtry = integer(), trees = integer(), min_n = integer(), tree_depth = integer(),
  learn_rate = numeric(), loss_reduction = numeric(), sample_size = numeric()
) %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-split-factors.Rmd"}
```

## Other details

```{r child = "template-spark-notes.Rmd"}
```

## References

 - Luraschi, J, K Kuo, and E Ruiz. 2019. _Mastering Spark with R_. O'Reilly Media

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

