```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("boost_tree", "lightgbm")`

## Tuning Parameters

```{r}
#| label: lightgbm-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("mtry", "trees", "tree_depth", "learn_rate", "min_n",  "loss_reduction"),
                 default = c("see below", 100L, -1, 0.1, 20, 0))

# For this model, this is the same for all modes
param <-
 boost_tree() |> 
  set_engine("lightgbm") |> 
  set_mode("regression") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: lightgbm-param-list
#| echo: false
#| results: asis
param$item
```

The `mtry` parameter gives the _number_ of predictors that will be randomly sampled at each split. The default is to use all predictors. 

Rather than as a number, [lightgbm::lgb.train()]'s `feature_fraction` argument encodes `mtry` as the _proportion_ of predictors that will be randomly sampled at each split. parsnip translates `mtry`, supplied as the _number_ of predictors, to a proportion under the hood. That is, the user should still supply the argument as `mtry` to `boost_tree()`, and do so in its sense as a number rather than a proportion; before passing `mtry` to [lightgbm::lgb.train()], parsnip will convert the `mtry` value to a proportion. 

Note that parsnip's translation can be overridden via the `counts` argument, supplied to `set_engine()`. By default, `counts` is set to `TRUE`, but supplying the argument `counts = FALSE` allows the user to supply `mtry` as a proportion rather than a number.

## Translation from parsnip to the original package (regression)

`r uses_extension("boost_tree", "lightgbm", "regression")`

```{r}
#| label: lightgbm-reg
boost_tree(
  mtry = integer(), trees = integer(), tree_depth = integer(), 
  learn_rate = numeric(), min_n = integer(), loss_reduction = numeric()
) |>
  set_engine("lightgbm") |>
  set_mode("regression") |>
  translate()
```

## Translation from parsnip to the original package (classification)

`r uses_extension("boost_tree", "lightgbm", "classification")`

```{r}
#| label: lightgbm-cls
boost_tree(
  mtry = integer(), trees = integer(), tree_depth = integer(), 
  learn_rate = numeric(), min_n = integer(), loss_reduction = numeric()
) |> 
  set_engine("lightgbm") |> 
  set_mode("classification") |> 
  translate()
```

[bonsai::train_lightgbm()] is a wrapper around [lightgbm::lgb.train()] (and other functions) that make it easier to run this model. 

## Other details

### Preprocessing

```{r}
#| child: template-tree-split-factors.Rmd
```

Non-numeric predictors (i.e., factors) are internally converted to numeric. In the classification context, non-numeric outcomes (i.e., factors) are also internally converted to numeric. 

### Interpreting `mtry`

```{r}
#| child: template-mtry-prop.Rmd
```

### Bagging

The `sample_size` argument is translated to the `bagging_fraction` parameter in the `param` argument of `lgb.train`. The argument is interpreted by lightgbm as a _proportion_ rather than a count, so bonsai internally reparameterizes the `sample_size` argument with [dials::sample_prop()] during tuning. 

To effectively enable bagging, the user would also need to set the `bagging_freq` argument to lightgbm. `bagging_freq` defaults to 0, which means bagging is disabled, and a `bagging_freq` argument of `k` means that the booster will perform bagging at every `k`th boosting iteration. Thus, by default, the `sample_size` argument would be ignored without setting this argument manually. Other boosting libraries, like xgboost, do not have an analogous argument to `bagging_freq` and use `k = 1` when the analogue to `bagging_fraction` is in $(0, 1)$. _bonsai will thus automatically set_ `bagging_freq = 1` _in_ `set_engine("lightgbm", ...)` if `sample_size` (i.e. `bagging_fraction`) is not equal to 1 and no `bagging_freq` value is supplied. This default can be overridden by setting the `bagging_freq` argument to `set_engine()` manually.

### Verbosity

bonsai quiets much of the logging output from [lightgbm::lgb.train()] by default. With default settings, logged warnings and errors will still be passed on to the user. To print out all logs during training, set `quiet = TRUE`.

## Sparse Data

```{r}
#| child: template-uses-sparse-data.Rmd
```

## Examples 

The "Introduction to bonsai" article contains [examples](https://bonsai.tidymodels.org/articles/bonsai.html) of `boost_tree()` with the `"lightgbm"` engine.

## References

 - [LightGBM: A Highly Efficient Gradient Boosting Decision Tree](https://papers.nips.cc/paper/2017/hash/6449f44a102fde848669bdd9eb6b76fa-Abstract.html)
 
- Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
