```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("boost_tree", "mboost")`

## Tuning Parameters

```{r mboost-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("mtry", "trees", "tree_depth", "min_n", "loss_reduction"),
                 default = c("see below", "100L", "2L", "10L", "0"))

param <-
  boost_tree() %>% 
  set_engine("mboost") %>% 
  set_mode("censored regression") %>%
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r mboost-param-list, echo = FALSE, results = "asis"}
param$item
```

The `mtry` parameter is related to the number of predictors. The default is to use all predictors.

## Translation from parsnip to the original package (censored regression)

`r uses_extension("boost_tree", "mboost", "censored regression")`

```{r mboost-creg}
library(censored)

boost_tree() %>% 
  set_engine("mboost") %>% 
  set_mode("censored regression") %>% 
  translate()
```

[blackboost_train()] is a wrapper around [mboost::blackboost()] (and other functions) that makes it easier to run this model. 

## Preprocessing requirements

```{r child = "template-tree-split-factors.Rmd"}
```

## References

 - Buehlmann P, Hothorn T. 2007. Boosting algorithms: regularization, prediction and model fitting. _Statistical Science_, 22(4), 477–505.

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
