# Engine Details

Engines may have pre-set default arguments when executing the model fit call. For this type of model, the template of the fit calls are below:

## xgboost

```{r xgboost-reg}
boost_tree() %>% 
  set_engine("xgboost") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r xgboost-csl}
boost_tree() %>% 
  set_engine("xgboost") %>% 
  set_mode("classification") %>% 
  translate()
```


## C5.0

```{r C5.0-csl}
boost_tree() %>% 
  set_engine("C5.0") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [C50::C5.0()] does not require factor predictors to be converted 
to indicator variables. 

## spark

```{r spark-reg}
boost_tree() %>% 
  set_engine("spark") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r spark-csl}
boost_tree() %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original names in each engine that has main parameters:

```{r echo = FALSE, results = "asis"}
parsnip::convert_args("boost_tree")
```

