```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("C5_rules", "C5.0")`

## Tuning Parameters

```{r C5.0-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("trees", "min_n"),
                 default = c("1L",       "2L"))

param <-
  C5_rules() %>% 
  set_engine("C5.0") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r C5.0-param-list, echo = FALSE, results = "asis"}
param$item
```

Note that C5.0 has a tool for _early stopping_ during boosting where less  iterations of boosting are performed than the number requested. `C5_rules()` turns this feature off (although it can be re-enabled using [C50::C5.0Control()]).

## Translation from parsnip to the underlying model call  (regression)

```{r C5.0-cls}
C5_rules(
  trees = integer(1),
  min_n = integer(1)
) %>%
  set_engine("C5.0") %>%
  set_mode("classification") %>%
  translate()
```

## Preprocessing requirements

```{r child = "template-tree-split-factors.Rmd"}
```

## References

 - Quinlan R (1992). "Learning with Continuous Classes." Proceedings of the 5th Australian Joint Conference On Artificial Intelligence, pp. 343-348.

 - Quinlan R (1993)."Combining Instance-Based and Model-Based Learning." Proceedings of the Tenth International Conference on Machine Learning, pp. 236-243.

 - Kuhn M and Johnson K (2013). _Applied Predictive Modeling_. Springer.
