```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("cubist_rules", "Cubist")`

## Tuning Parameters

```{r cubist-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("committees", "neighbors",  "max_rules"),
                 default = c("1L",                "0L", "NA_integer"))

param <-
  cubist_rules() %>% 
  set_engine("Cubist") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r cubist-param-list, echo = FALSE, results = "asis"}
param$item
```


## Translation from parsnip to the underlying model call  (regression)

```{r cubist-reg}
cubist_rules(
  committees = integer(1),
  neighbors = integer(1),
  max_rules = integer(1)
) %>%
  set_engine("Cubist") %>%
  set_mode("regression") %>%
  translate()
```

## Preprocessing requirements

```{r child = "template-tree-split-factors.Rmd"}
```

## References

 - Quinlan R (1992). "Learning with Continuous Classes." Proceedings of the 5th Australian Joint Conference On Artificial Intelligence, pp. 343-348.

 - Quinlan R (1993)."Combining Instance-Based and Model-Based Learning." Proceedings of the Tenth International Conference on Machine Learning, pp. 236-243.

 - Kuhn M and Johnson K (2013). _Applied Predictive Modeling_. Springer.
