```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("decision_tree", "rpart")`

## Tuning Parameters

```{r}
#| label: rpart-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "min_n", "cost_complexity"),
                 default = c("30L", "2L", "0.01"))

param <-
 decision_tree() |> 
  set_engine("rpart") |> 
  set_mode("regression") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: rpart-param-list
#| echo: false
#| results: asis
param$item
```

## Translation from parsnip to the original package (classification)

```{r}
#| label: rpart-cls
decision_tree(tree_depth = integer(1), min_n = integer(1), cost_complexity = double(1)) |> 
  set_engine("rpart") |> 
  set_mode("classification") |> 
  translate()
```


## Translation from parsnip to the original package (regression)

```{r}
#| label: rpart-reg
decision_tree(tree_depth = integer(1), min_n = integer(1), cost_complexity = double(1)) |> 
  set_engine("rpart") |> 
  set_mode("regression") |> 
  translate()
```


## Translation from parsnip to the original package (censored regression)

`r uses_extension("decision_tree", "rpart", "censored regression")`

```{r}
#| label: rpart-cens-reg
library(censored)

decision_tree(
  tree_depth = integer(1),
  min_n = integer(1),
  cost_complexity = double(1)
) |> 
  set_engine("rpart") |> 
  set_mode("censored regression") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Other details

```{r}
#| child: template-survival-mean.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#decision-tree-rpart) for `decision_tree()` with the `"rpart"` engine.

## References

-   Kuhn, M, and K Johnson. 2013. *Applied Predictive Modeling*. Springer.

