# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. For this type of model, the template of the fit calls are below:

## rpart

```{r rpart-reg}
decision_tree() %>% 
  set_engine("rpart") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r rpart-csl}
decision_tree() %>% 
  set_engine("rpart") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [rpart::rpart()] does not require factor predictors to be converted  to indicator variables. `fit()` does not affect the encoding of the predictor values (i.e. factors stay factors) for this model

## C5.0

```{r C5.0-csl}
decision_tree() %>% 
  set_engine("C5.0") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [C50::C5.0()] does not require factor predictors to be converted to indicator variables. `fit()` does not affect the encoding of the predictor values (i.e. factors stay factors) for this model 

## spark

```{r spark-reg}
decision_tree() %>% 
  set_engine("spark") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r spark-csl}
decision_tree() %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```

`fit()` does not affect the encoding of the predictor values (i.e. factors stay factors) for this model

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original names in each engine that has main parameters. Each engine typically has a different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_decision_tree <- function() {
  tibble::tribble(
    ~model,         ~engine,          ~parsnip,                ~original,  ~default,
    "decision_tree", "rpart",      "tree_depth",               "maxdepth", get_arg("rpart", "rpart.control", "maxdepth"),
    "decision_tree", "rpart",           "min_n",               "minsplit", get_arg("rpart", "rpart.control", "minsplit"),
    "decision_tree", "rpart", "cost_complexity",                     "cp", get_arg("rpart", "rpart.control", "cp"),
    "decision_tree",  "C5.0",           "min_n",               "minCases", get_arg("C50", "C5.0Control", "minCases"),
    "decision_tree", "spark",      "tree_depth",              "max_depth", get_arg("sparklyr", "ml_decision_tree", "max_depth"),
    "decision_tree", "spark",           "min_n", "min_instances_per_node", get_arg("sparklyr", "ml_decision_tree", "min_instances_per_node"),
  )
}
convert_args("decision_tree")
```

