```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("decision_tree", "partykit")`

## Tuning Parameters

```{r}
#| label: partykit-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "min_n"),
                 default = c("see below", "20L"))

param <-
 decision_tree() |> 
  set_engine("partykit") |> 
  set_mode("regression") |> 
  make_parameter_list(defaults) |> 
  distinct()
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: partykit-param-list
#| echo: false
#| results: asis
param$item
```

The `tree_depth` parameter defaults to `0` which means no restrictions are applied to tree depth.

An engine-specific parameter for this model is: 

 * `mtry`: the number of predictors, selected at random, that are evaluated for splitting. The default is to use all predictors.

## Translation from parsnip to the original package (regression)

`r uses_extension("decision_tree", "partykit", "regression")`

```{r}
#| label: partykit-creg
library(bonsai)

decision_tree(tree_depth = integer(1), min_n = integer(1)) |> 
  set_engine("partykit") |> 
  set_mode("regression") |> 
  translate()
```

## Translation from parsnip to the original package (classification)

`r uses_extension("decision_tree", "partykit", "classification")`

```{r}
#| label: partykit-class
library(bonsai)

decision_tree(tree_depth = integer(1), min_n = integer(1)) |> 
  set_engine("partykit") |> 
  set_mode("classification") |> 
  translate()
```

`parsnip::ctree_train()` is a wrapper around [partykit::ctree()] (and other functions) that makes it easier to run this model. 

## Translation from parsnip to the original package (censored regression)

`r uses_extension("decision_tree", "partykit", "censored regression")`

```{r}
#| label: party-creg
library(censored)

decision_tree(tree_depth = integer(1), min_n = integer(1)) |> 
  set_engine("partykit") |> 
  set_mode("censored regression") |> 
  translate()
```

`censored::cond_inference_surv_ctree()` is a wrapper around [partykit::ctree()] (and other functions) that makes it easier to run this model. 

## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```

## Other details

```{r}
#| child: template-survival-median.Rmd
```

## References

 - [partykit: A Modular Toolkit for Recursive Partytioning in R](https://jmlr.org/papers/v16/hothorn15a.html)

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
