```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("decision_tree", "party")`

## Tuning Parameters

```{r party-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "min_n"),
                 default = c("see below", "20L"))

param <-
 decision_tree() %>% 
  set_engine("party") %>% 
  set_mode("censored regression") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r party-param-list, echo = FALSE, results = "asis"}
param$item
```

The `tree_depth` parameter defaults to `0` which means no restrictions are applied to tree depth.

An engine specific parameter for this model is: 

 * `mtry`: the number of predictors, selected at random, that are evaluated for splitting. The default is to use all predictors.

## Translation from parsnip to the original package (censored regression)

```{r party-creg}
decision_tree(tree_depth = integer(1), min_n = integer(1)) %>% 
  set_engine("party") %>% 
  set_mode("censored regression") %>% 
  translate()
```

[cond_inference_surv_ctree()] is a wrapper around [party::ctree()] (and other functions) that makes it easier to run this model. 

## Preprocessing requirements

```{r child = "template-tree-split-factors.Rmd"}
```

## References

 - Hothorn T, Hornik K, Zeileis A. 2006. Unbiased Recursive Partitioning: A Conditional Inference Framework. _Journal of Computational and Graphical Statistics_, 15(3), 651–674.

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
