```{r, child="aaa.Rmd", include=FALSE}
```

`r descr_models("decision_tree", "rpartScore")`

## Tuning parameters

```{r rpartScore-param-info, echo=FALSE}
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "min_n", "cost_complexity"),
                 default = c("30L", "2L", "0.01"))

param <-
  decision_tree() |> 
  set_engine("rpartScore") |> 
  set_mode("classification") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r, rpartScore-param-list, echo=FALSE, results='asis'}
param$item
```

## Translation from parsnip to the original package

```{r, rpartScore-cls}
#| label: rpart-cls
decision_tree(tree_depth = integer(1), min_n = integer(1), cost_complexity = double(1)) |> 
  set_engine("rpartScore") |> 
  set_mode("classification") |> 
  translate()
```

<!--
REVIEW: Add any needed sections here.
-->

## References

- Galimberti G, Soffritti G, Di Maso M. 2012. Classification Trees for Ordinal Responses in R: The rpartScore Package. _Journal of Statistical Software_ 47(10):1-25. \doi{10.18637/jss.v047.i10}.

- Kuhn, M, and K Johnson. 2013. *Applied Predictive Modeling*. Springer.
