```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("discrim_regularized", "klaR")`

## Tuning Parameters


```{r}
#| label: klaR-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("frac_identity", "frac_common_cov"),
                 default = c("(see below)", "(see below)"))

param <-
  discrim_regularized() |> 
  set_engine("klaR") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameter:

```{r}
#| label: klaR-param-list
#| echo: false
#| results: asis
param$item
```

Some special cases for the RDA model: 

* `frac_identity = 0` and `frac_common_cov = 1` is a linear discriminant analysis (LDA) model. 

* `frac_identity = 0` and `frac_common_cov = 0` is a quadratic discriminant analysis (QDA) model. 



## Translation from parsnip to the original package

`r uses_extension("discrim_regularized", "klaR", "classification")`

```{r}
#| label: klaR-cls
library(discrim)

discrim_regularized(frac_identity = numeric(0), frac_common_cov = numeric(0)) |> 
  set_engine("klaR") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-zv-conditional.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## References

 - Friedman, J (1989). Regularized Discriminant Analysis. _Journal of the American Statistical Association_, 84, 165-175.

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
