```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("discrim_flexible", "earth")`

## Tuning Parameters

```{r}
#| label: earth-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("num_terms", "prod_degree", "prune_method"),
                 default = c("(see below)", "1L", "'backward'"))

param <-
  discrim_flexible() |> 
  set_engine("earth") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameter:

```{r}
#| label: earth-param-list
#| echo: false
#| results: asis
param$item
```

The default value of `num_terms` depends on the number of columns (`p`): `min(200, max(20, 2 * p)) + 1`. Note that `num_terms = 1` is an intercept-only model. 

## Translation from parsnip to the original package

`r uses_extension("discrim_flexible", "earth", "classification")`

```{r}
#| label: earth-cls
library(discrim)

discrim_flexible(
  num_terms = integer(0),
  prod_degree = integer(0),
  prune_method = character(0)
) |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## References

 - Hastie, Tibshirani & Buja (1994) Flexible Discriminant Analysis by Optimal 
   Scoring, _Journal of the American Statistical Association_, 89:428, 1255-1270
   
 - Friedman (1991). Multivariate Adaptive Regression Splines. _The Annals of Statistics_, 19(1), 1-67.
