```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("discrim_linear", "sda")`

## Tuning Parameters

This engine has no tuning parameter arguments in [discrim_linear()]. 

However, there are a few engine-specific parameters that can be set or optimized when calling [set_engine()]:

* `lambda`: the shrinkage parameters for the correlation matrix. This maps to the \pkg{dials} parameter [dials::shrinkage_correlation()].

* `lambda.var`: the shrinkage parameters for the predictor variances. This maps to [dials::shrinkage_variance()].

* `lambda.freqs`: the shrinkage parameters for the class frequencies. This maps to [dials::shrinkage_frequencies()].

* `diagonal`: a logical to make the model covariance diagonal or not. This maps to [dials::diagonal_covariance()].

## Translation from parsnip to the original package

`r uses_extension("discrim_linear", "sda", "classification")`

```{r}
#| label: sda-cls
library(discrim)

discrim_linear() |> 
  set_engine("sda") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-zv.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## References

 - Ahdesmaki, A., and K. Strimmer. 2010. Feature selection in omics prediction problems using cat scores and false non-discovery rate control. Ann. Appl. Stat. 4: 503-519. [Preprint](https://arxiv.org/abs/0903.2003).
