```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("discrim_linear", "mda")`

## Tuning Parameters


```{r}
#| label: mda-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("penalty"),
                 default = c("1.0"))

param <-
  discrim_linear() |> 
  set_engine("mda") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameter:

```{r}
#| label: mda-param-list
#| echo: false
#| results: asis
param$item
```

## Translation from parsnip to the original package

`r uses_extension("discrim_linear", "mda", "classification")`

```{r}
#| label: mda-cls
library(discrim)

discrim_linear(penalty = numeric(0)) |> 
  set_engine("mda") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-zv.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## References

 - Hastie, Tibshirani & Buja (1994) Flexible Discriminant Analysis by Optimal 
   Scoring, _Journal of the American Statistical Association_, 89:428, 1255-1270
