```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("discrim_linear", "sparsediscrim")`

## Tuning Parameters

```{r}
#| label: sparsediscrim-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("regularization_method"),
                 default = c("'diagonal'"))

param <-
  discrim_linear() |> 
  set_engine("sparsediscrim") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameter:

```{r}
#| label: mda-param-list
#| echo: false
#| results: asis
param$item
```

The possible values of this parameter, and the functions that they execute, are:

* `"diagonal"`: [sparsediscrim::lda_diag()]
* `"min_distance"`: [sparsediscrim::lda_emp_bayes_eigen()]
* `"shrink_mean"`: [sparsediscrim::lda_shrink_mean()]
* `"shrink_cov"`: [sparsediscrim::lda_shrink_cov()]

## Translation from parsnip to the original package

`r uses_extension("discrim_linear", "sparsediscrim", "classification")`

```{r}
#| label: sparsediscrim-cls
library(discrim)

discrim_linear(regularization_method = character(0)) |> 
  set_engine("sparsediscrim") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-zv.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## References


 - `lda_diag()`: Dudoit, Fridlyand and Speed (2002) Comparison of Discrimination Methods for the Classification of Tumors Using Gene Expression Data, _Journal of the American Statistical Association_, 97:457, 77-87. 
 
 - `lda_shrink_mean()`: Tong, Chen, Zhao, Improved mean estimation and its application to diagonal discriminant analysis, _Bioinformatics_, Volume 28, Issue 4, 15 February 2012, Pages 531-537.
 
 - `lda_shrink_cov()`: Pang, Tong and Zhao (2009), Shrinkage-based Diagonal Discriminant Analysis and Its Applications in High-Dimensional Data. _Biometrics_, 65, 1021-1029.

 - `lda_emp_bayes_eigen()`: Srivistava and Kubokawa (2007), Comparison of Discrimination Methods for High Dimensional Data, _Journal of the Japan Statistical Society_, 37:1, 123-134. 
