```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("gen_additive_mod", "mgcv")`

## Tuning Parameters


```{r}
#| label: earth-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("select_features", "adjust_deg_free"),
                 default = c("FALSE", "1.0"))

param <-
  gen_additive_mod() |> 
  set_engine("mgcv") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: earth-param-list
#| echo: false
#| results: asis
param$item
```


## Translation from parsnip to the original package  (regression)

```{r}
#| label: glm-reg
gen_additive_mod(adjust_deg_free = numeric(1), select_features = logical(1)) |> 
  set_engine("mgcv") |> 
  set_mode("regression") |> 
  translate()
```

## Translation from parsnip to the original package  (classification)

```{r}
#| label: glm-cls
gen_additive_mod(adjust_deg_free = numeric(1), select_features = logical(1)) |> 
  set_engine("mgcv") |> 
  set_mode("classification") |> 
  translate()
```

## Model fitting

This model should be used with a model formula so that smooth terms can be specified. For example:

```{r}
#| include: false
library(mgcv)
```
```{r}
library(mgcv)
gen_additive_mod() |> 
  set_engine("mgcv") |> 
  set_mode("regression") |> 
  fit(mpg ~ wt + gear + cyl + s(disp, k = 10), data = mtcars)
```

The smoothness of the terms will need to be manually specified (e.g., using `s(x, df = 10)`) in the formula. Tuning can be accomplished using the `adjust_deg_free` parameter. 


When using a workflow, pass the _model formula_ to [workflows::add_model()]'s `formula` argument, and a simplified _preprocessing formula_ elsewhere.

```{r}
spec <- 
  gen_additive_mod() |> 
  set_engine("mgcv") |> 
  set_mode("regression")

workflow() |> 
  add_model(spec, formula = mpg ~ wt + gear + cyl + s(disp, k = 10)) |> 
  add_formula(mpg ~ wt + gear + cyl + disp) |> 
  fit(data = mtcars) |> 
  extract_fit_engine()
```

To learn more about the differences between these formulas, see [`?model_formula`][parsnip::model_formula].

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```

## References

 - Ross, W. 2021. [_Generalized Additive Models in R: A Free, Interactive Course using mgcv_](https://noamross.github.io/gams-in-r-course/)
 
 - Wood, S. 2017. _Generalized Additive Models: An Introduction with R_. Chapman and Hall/CRC.
