```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("linear_reg", "quantreg")`

This model has the same structure as the model fit by `lm()`, but instead of optimizing the sum of squared errors, it optimizes "quantile loss" in order to produce better estimates of the predictive distribution. 

## Tuning Parameters

This engine has no tuning parameters. 

## Translation from parsnip to the original package

This model only works with the `"quantile regression"` model and requires users to specify which areas of the distribution to predict via the `quantile_levels` argument. For example: 

```{r}
#| label: quantreg-reg
linear_reg() |> 
  set_engine("quantreg") |> 
  set_mode("quantile regression", quantile_levels = (1:3) / 4) |> 
  translate()
```

## Output format

When multiple quantile levels are predicted, there are multiple predicted values for each row of new data. The `predict()` method for this mode produces a column named `.pred_quantile` that has a special class of `"quantile_pred"`, and it contains the predictions for each row. 

For example: 

```{r}
#| label: example
library(modeldata)
rlang::check_installed("quantreg")

n <- nrow(Chicago)
Chicago <- Chicago |> select(ridership, Clark_Lake)

Chicago_train <- Chicago[1:(n - 7), ]
Chicago_test  <- Chicago[(n - 6):n, ]

qr_fit <- 
  linear_reg() |> 
  set_engine("quantreg") |> 
  set_mode("quantile regression", quantile_levels = (1:3) / 4) |> 
  fit(ridership ~ Clark_Lake, data = Chicago_train)
qr_fit

qr_pred <- predict(qr_fit, Chicago_test)
qr_pred
```

We can unnest these values and/or convert them to a rectangular format:  

```{r}
#| label: example-format
as_tibble(qr_pred$.pred_quantile)

as.matrix(qr_pred$.pred_quantile)
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#linear-reg-quantreg) for `linear_reg()` with the `"quantreg"` engine.

## References

 - Waldmann, E. (2018). Quantile regression: a short story on how and why. _Statistical Modelling_, 18(3-4), 203-218.
