```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("linear_reg", "keras")`

## Tuning Parameters

```{r keras-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty"),
                 default = c("0.0"))

param <-
  linear_reg() %>% 
  set_engine("keras") %>% 
  tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>%  
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  dplyr::mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has one tuning parameter:

```{r keras-param-list, echo = FALSE, results = "asis"}
param$item
```

For `penalty`, the amount of regularization is _only_ L2 penalty (i.e., ridge or weight decay). 

## Translation from parsnip to the original package

```{r keras-csl}
linear_reg(penalty = double(1)) %>% 
  set_engine("keras") %>% 
  translate()
```

[keras_mlp()] is a parsnip wrapper around keras code for neural networks. This model fits a linear regression as a network with a single hidden unit. 

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#linear-reg-keras) for `linear_reg()` with the `"keras"` engine.

## References

 - Hoerl, A., & Kennard, R. (2000). _Ridge Regression: Biased Estimation for Nonorthogonal Problems_. Technometrics, 42(1), 80-86. 

