```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("linear_reg", "stan")`

## Tuning Parameters

This model has no tuning parameters.

## Important engine-specific options

Some relevant arguments that can be passed to `set_engine()`: 

 * `chains`: A positive integer specifying the number of Markov chains. The default is 4.
 * `iter`: A positive integer specifying the number of iterations for each chain (including warmup). The default is 2000.
 * `seed`: The seed for random number generation. 
 * `cores`: Number of cores to use when executing the chains in parallel.
 * `prior`: The prior distribution for the (non-hierarchical) regression coefficients. The `stan` engine does not fit any hierarchical terms. See the `stan_glmer` engine from the `multilevelmod` package for that type of model. 
 * `prior_intercept`: The prior distribution for the intercept (after centering all predictors). 
 

## Translation from parsnip to the original package

```{r stan-csl}
linear_reg() %>% 
  set_engine("stan") %>% 
  set_mode("regression") %>% 
  translate()
```

## Preprocessing requirements

The only preprocessing required for this model is that factor/categorical predictors need to be converted to numeric values (e.g., dummy or indicator variables). When using the formula method via [fit.model_spec()], `parsnip` will convert these data if required.

## Other details

The model can accept case weights. 

For prediction, the `stan` engine can compute posterior  intervals analogous to
confidence and prediction intervals. In  these instances, the units are the
original outcome and when  `std_error = TRUE`, the standard deviation of the
posterior  distribution (or posterior predictive distribution as  appropriate) is
returned.

## References

 - McElreath, R. 2020 _Statistical Rethinking_. CRC Press.
