```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("linear_reg", "glmnet")`

## Tuning Parameters

```{r glmnet-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("see below", "1.0"))

param <-
  get_from_env("linear_reg_args") %>% 
  dplyr::filter(engine == "glmnet") %>% 
  dplyr::mutate(
    dials = purrr::map(func, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameters:

```{r glmnet-param-list, echo = FALSE, results = "asis"}
param$item
```

A value of `mixture = 1` corresponds to a pure lasso model, while `mixture = 0` indicates ridge regression.

For more details about the `glmnet` model, see [glmnet-details]

## Translation from parsnip to the original package

```{r glmnet-csl}
linear_reg(penalty = double(1), mixture = double(1)) %>% 
  set_engine("glmnet") %>% 
  set_mode("regression") %>% 
  translate()
```

## Preprocessing requirements

Factor/categorical predictors need to be converted to numeric values (e.g., dummy or indicators variables). When using the formula method via [fit.model_spec()], `parsnip` will convert these data if required.

Also, predictors should have the same scale. One way to achieve this is to center and scale each so that each predictors have mean zero and a variance of one. By default, `glmnet()` uses the argument `standardize = TRUE` to center and scale the data. 

## References

 - Hastie, T, R Tibshirani, and M Wainwright. 2015. _Statistical Learning with Sparsity_. CRC Press.
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

