```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("linear_reg", "stan_glmer")`

## Tuning Parameters

This model has no tuning parameters.

## Important engine-specific options

Some relevant arguments that can be passed to `set_engine()`: 

 * `chains`: A positive integer specifying the number of Markov chains. The default is 4.
 * `iter`: A positive integer specifying the number of iterations for each chain (including warmup). The default is 2000.
 * `seed`: The seed for random number generation. 
 * `cores`: Number of cores to use when executing the chains in parallel.
 * `prior`: The prior distribution for the (non-hierarchical) regression coefficients. 
 * `prior_intercept`: The prior distribution for the intercept (after centering all predictors). 
 
See `?rstanarm::stan_glmer` and `?rstan::sampling` for more information.

## Translation from parsnip to the original package

`r uses_extension("linear_reg", "stan_glmer", "regression")`

```{r}
#| label: stan_glmer-csl
library(multilevelmod)

linear_reg() |> 
  set_engine("stan_glmer") |> 
  set_mode("regression") |> 
  translate()
```

```{r}
#| child: template-no-pooling.Rmd
```

## Preprocessing requirements

There are no specific preprocessing needs. However, it is helpful to keep the clustering/subject identifier column as factor or character (instead of making them into dummy variables). See the examples in the next section. 

## Other details

The model can accept case weights. 

With parsnip, we suggest using the formula method when fitting: 

```r
library(tidymodels)
data("riesby")

linear_reg() |> 
  set_engine("stan_glmer") |> 
  fit(depr_score ~ week + (1|subject), data = riesby)
```

When using tidymodels infrastructure, it may be better to use a workflow. In this case, you can add the appropriate columns using `add_variables()` then supply the typical formula when adding the model: 

```r
library(tidymodels)

glmer_spec <- 
  linear_reg() |> 
  set_engine("stan_glmer")

glmer_wflow <- 
  workflow() |> 
  # The data are included as-is using:
  add_variables(outcomes = depr_score, predictors = c(week, subject)) |> 
  add_model(glmer_spec, formula = depr_score ~ week + (1|subject))

fit(glmer_wflow, data = riesby)
```

For prediction, the `"stan_glmer"` engine can compute posterior intervals analogous to confidence and prediction intervals. In  these instances, the units are the original outcome. When  `std_error = TRUE`, the standard deviation of the posterior  distribution (or posterior predictive distribution as  appropriate) is returned.

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## References

 - McElreath, R. 2020 _Statistical Rethinking_. CRC Press.

 - Sorensen, T, Vasishth, S. 2016. Bayesian linear mixed models using Stan: A tutorial for psychologists, linguists, and cognitive scientists, 	arXiv:1506.06201.
