```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("linear_reg", "gls")`

## Tuning Parameters

This model has no tuning parameters.

## Translation from parsnip to the original package

`r uses_extension("linear_reg", "gls", "regression")`

```{r}
#| label: gls-csl
library(multilevelmod)

linear_reg() |> 
  set_engine("gls") |> 
  set_mode("regression") |> 
  translate()
```


## Preprocessing requirements

There are no specific preprocessing needs. However, it is helpful to keep the clustering/subject identifier column as factor or character (instead of making them into dummy variables). See the examples in the next section. 

## Other details

The model can accept case weights. 

With parsnip, we suggest using the _fixed effects_ formula method when fitting, but the details of the correlation structure should be passed to `set_engine()` since it is an irregular (but required) argument:

```{r}
library(tidymodels)
# load nlme to be able to use the `cor*()` functions
library(nlme)

data("riesby")

linear_reg() |> 
  set_engine("gls", correlation =  corCompSymm(form = ~ 1 | subject)) |> 
  fit(depr_score ~ week, data = riesby)
```

When using tidymodels infrastructure, it may be better to use a workflow. In this case, you can add the appropriate columns using `add_variables()` then supply the typical formula when adding the model: 

```r
library(tidymodels)

gls_spec <- 
  linear_reg() |> 
  set_engine("gls", correlation =  corCompSymm(form = ~ 1 | subject))

gls_wflow <- 
  workflow() |> 
  # The data are included as-is using:
  add_variables(outcomes = depr_score, predictors = c(week, subject)) |> 
  add_model(gls_spec, formula = depr_score ~ week)

fit(gls_wflow, data = riesby)
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## References

- J Pinheiro, and D Bates. 2000. _Mixed-effects models in S and S-PLUS_. Springer, New York, NY
 
