```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("linear_reg", "h2o")`

## Tuning Parameters

```{r h2o-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("0", "see below"))

param <-
linear_reg() %>% 
  set_engine("h2o") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r h2o-param-list, echo = FALSE, results = "asis"}
param$item
```

By default [h2o::h2o.glm()] applies no regularization and `penalty` is set to zero. When the engine parameter `solver` is set to `'L-BFGS'`, `mixture` defaults to 0 (ridge regression) and 0.5 otherwise. 

## Translation from parsnip to the original package

[agua::h2o_train_glm()] for `linear_reg()` is a wrapper around [h2o::h2o.glm()] with `family = "gaussian"`.


```{r h2o-csl}
linear_reg(penalty = 1, mixture = 0.5) %>% 
  set_engine("h2o") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```
By default, [h2o::h2o.glm()] uses the argument `standardize = TRUE` to center and scale the data. 

