```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("linear_reg", "glm")`

## Tuning Parameters

This engine has no tuning parameters but you can set the `family` parameter (and/or `link`) as an engine argument (see below). 

## Translation from parsnip to the original package

```{r}
#| label: glm-reg
linear_reg() |> 
  set_engine("glm") |> 
  translate()
```

To use a non-default `family` and/or `link`, pass in as an argument to `set_engine()`:

```{r}
#| label: glm-reg-engine
linear_reg() |> 
  set_engine("glm", family = stats::poisson(link = "sqrt")) |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

_However_, the documentation in [stats::glm()] assumes that is specific type of case weights are being used:"Non-NULL weights can be used to indicate that different observations have different dispersions (with the values in weights being inversely proportional to the dispersions); or equivalently, when the elements of weights are positive integers `w_i`, that each response `y_i` is the mean of `w_i` unit-weight observations. For a binomial GLM prior weights are used to give the number of trials when the response is the proportion of successes: they would rarely be used for a Poisson GLM."

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```


## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#linear-reg-glm) for `linear_reg()` with the `"glm"` engine.

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
