```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("linear_reg", "lme")`

## Tuning Parameters

This model has no tuning parameters.

## Translation from parsnip to the original package

`r uses_extension("linear_reg", "lme", "regression")`

```{r}
#| label: lme-csl
library(multilevelmod)

linear_reg() |> 
  set_engine("lme") |> 
  set_mode("regression") |> 
  translate()
```

```{r}
#| child: template-no-pooling.Rmd
```

## Preprocessing requirements

There are no specific preprocessing needs. However, it is helpful to keep the clustering/subject identifier column as factor or character (instead of making them into dummy variables). See the examples in the next section. 

## Other details

The model can accept case weights. 

With parsnip, we suggest using the _fixed effects_ formula method when fitting, but the random effects formula should be passed to `set_engine()` since it is an irregular (but required) argument:

```r
library(tidymodels)
data("riesby")

linear_reg() |> 
  set_engine("lme", random =  ~ 1|subject) |> 
  fit(depr_score ~ week, data = riesby)
```

When using tidymodels infrastructure, it may be better to use a workflow. In this case, you can add the appropriate columns using `add_variables()` then supply the typical formula when adding the model: 

```r
library(tidymodels)

lme_spec <- 
  linear_reg() |> 
  set_engine("lme", random =  ~ 1|subject)

lme_wflow <- 
  workflow() |> 
  # The data are included as-is using:
  add_variables(outcomes = depr_score, predictors = c(week, subject)) |> 
  add_model(lme_spec, formula = depr_score ~ week)

fit(lme_wflow, data = riesby)
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## References

- J Pinheiro, and D Bates. 2000. _Mixed-effects models in S and S-PLUS_. Springer, New York, NY
 
- West, K, Band Welch, and A Galecki. 2014. _Linear Mixed Models: A Practical Guide Using Statistical Software_. CRC Press.
 
- Thorson, J, Minto, C. 2015, Mixed effects: a unifying framework for statistical modelling in fisheries biology. _ICES Journal of Marine Science_, Volume 72, Issue 5, Pages 1245–1256.
  
- Harrison, XA, Donaldson, L, Correa-Cano, ME, Evans, J, Fisher, DN, Goodwin, CED, Robinson, BS, Hodgson, DJ, Inger, R. 2018. _A brief introduction to mixed effects modelling and multi-model inference in ecology_. PeerJ 6:e4794. 
  
- DeBruine LM, Barr DJ. Understanding Mixed-Effects Models Through Data Simulation. 2021. _Advances in Methods and Practices in Psychological Science_.   
  
