```{r, child = "aaa.Rmd", include = FALSE}
```


`r descr_models("logistic_reg", "h2o")`

## Tuning Parameters

```{r h2o-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("see below", "see below"))

param <-
logistic_reg() |> 
  set_engine("h2o") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r h2o-param-list, echo = FALSE, results = "asis"}
param$item
```

```{r, child = "template-h2o-glm-penalty.Rmd", include = FALSE}
```


## Translation from parsnip to the original package

[agua::h2o_train_glm()] for `logistic_reg()` is a wrapper around [h2o::h2o.glm()]. h2o will automatically picks the link function and distribution family or binomial responses. 

```{r h2o-reg}
logistic_reg() |> 
  set_engine("h2o") |> 
  translate()
```

To use a non-default argument in [h2o::h2o.glm()], pass in as an engine argument to `set_engine()`:

```{r h2o-reg-engine}
logistic_reg() |> 
  set_engine("h2o", compute_p_values = TRUE) |> 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

By default, [h2o::h2o.glm()] uses the argument `standardize = TRUE` to center and scale all numeric columns. 


## Initializing h2o 

```{r child = "template-h2o-init.Rmd"}
```

## Saving fitted model objects

```{r child = "template-bundle.Rmd"}
```
