```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("logistic_reg", "LiblineaR")`

## Tuning Parameters

```{r}
#| label: LiblineaR-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("see below", "0"))

param <-
logistic_reg() |> 
  set_engine("LiblineaR") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: LiblineaR-param-list
#| echo: false
#| results: asis
param$item
```

For `LiblineaR` models, the value for `mixture` can either be 0 (for ridge) or 1 (for lasso) but not other intermediate values. In the [LiblineaR::LiblineaR()] documentation, these correspond to types 0 (L2-regularized) and 6 (L1-regularized).

Be aware that the `LiblineaR` engine regularizes the intercept. Other regularized regression models do not, which will result in different parameter estimates.

## Translation from parsnip to the original package

```{r}
#| label: LiblineaR-cls
logistic_reg(penalty = double(1), mixture = double(1)) |> 
  set_engine("LiblineaR") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

## Sparse Data

```{r}
#| child: template-uses-sparse-data.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#logistic-reg-LiblineaR) for `logistic_reg()` with the `"LiblineaR"` engine.

## References

 - Hastie, T, R Tibshirani, and M Wainwright. 2015. _Statistical Learning with Sparsity_. CRC Press.
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

