# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below.

## glm

```{r glm-reg}
logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification") %>% 
  translate()
```

## glmnet

```{r glmnet-csl}
logistic_reg() %>% 
  set_engine("glmnet") %>% 
  set_mode("classification") %>% 
  translate()
```

For `glmnet` models, the full regularization path is always fit regardless of the
value given to `penalty`. Also, there is the option to pass  multiple values (or
no values) to the `penalty` argument. When using the  `predict()` method in these
cases, the return value depends on  the value of `penalty`. When using
`predict()`, only a single  value of the penalty can be used. When predicting on
multiple  penalties, the `multi_predict()` function can be used. It  returns a
tibble with a list column called `.pred` that contains  a tibble with all of the
penalty results.

## LiblineaR

```{r liblinear-reg}
logistic_reg() %>% 
  set_engine("LiblineaR") %>% 
  set_mode("classification") %>% 
  translate()
```

For `LiblineaR` models, the value for `mixture` can either be 0 (for ridge) or 1 
(for lasso) but not other intermediate values. In the `LiblineaR` documentation, 
these correspond to types 0 (L2-regularized) and 6 (L1-regularized).

Be aware that the `LiblineaR` engine regularizes the intercept. Other 
regularized regression models do not, which will result in different parameter estimates.

## stan

```{r stan-reg}
logistic_reg() %>% 
  set_engine("stan") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that the `refresh` default prevents logging of the estimation process.
Change this value in `set_engine()` will show the logs.

For prediction, the `stan` engine can compute posterior  intervals analogous to
confidence and prediction intervals. In  these instances, the units are the
original outcome and when  `std_error = TRUE`, the standard deviation of the
posterior  distribution (or posterior predictive distribution as  appropriate) is
returned.

## spark

```{r spark-reg}
logistic_reg() %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```

## keras

```{r keras-reg}
logistic_reg() %>% 
  set_engine("keras") %>% 
  set_mode("classification") %>% 
  translate()
```


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_logistic_reg <- function() {
  tibble::tribble(
    ~model,          ~engine,     ~parsnip,            ~original,  ~default,
    "logistic_reg",  "glmnet",    "mixture",              "alpha",  get_arg("glmnet", "glmnet", "alpha"),
    "logistic_reg",  "LiblineaR", "mixture",              "type",   "0",
    "logistic_reg",  "spark",     "penalty",          "reg_param",  get_arg("sparklyr", "ml_logistic_regression", "reg_param"),
    "logistic_reg",  "spark",     "mixture",  "elastic_net_param",  get_arg("sparklyr", "ml_logistic_regression", "elastic_net_param"),
    "logistic_reg",  "keras",     "penalty",            "penalty",  get_arg("parsnip", "keras_mlp", "penalty"),
  )
}
convert_args("logistic_reg")
```
