```{r, child = "aaa.Rmd", include = FALSE}
```


`r descr_models("logistic_reg", "h2o")`

## Tuning Parameters

```{r LiblineaR-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("0", "0"))

param <-
logistic_reg() %>% 
  set_engine("h2o") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r h2o-param-list, echo = FALSE, results = "asis"}
param$item
```


## Translation from parsnip to the original package

`agua` uses the [agua::h2o_train_glm()] wrapper function for fitting the logistic regression model, which calls [h2o::h2o.glm()]. h2o will automatically picks the link function and distribution family or binomial responses. 

```{r h2o-reg}
logistic_reg() %>% 
  set_engine("h2o") %>% 
  translate()
```

To use a non-default argument in [h2o::h2o.glm()], pass in as an engine argument to `set_engine()`:

```{r glm-reg-engine}
logistic_reg() %>% 
  set_engine("h2o", compute_p_values = TRUE) %>% 
  translate()
```

Other h2o engine arguments of interest: 


- `solver`: The solver method used in optimization, the default `"auto"` works well in most cases


## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

By default, [h2o::h2o.glm()] uses the argument `standardize = TRUE` to center and scale all numeric columns. 
