```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("logistic_reg", "gee")`

## Tuning Parameters

This model has no formal tuning parameters. It might be beneficial to determine the appropriate correlation structure to use. However, this typically does not affect the predicted value of the model but does have an effect on the inferential results and parameter covariance values. 

## Translation from parsnip to the original package

`r uses_extension("logistic_reg", "gee", "classification")`

```{r gee-csl}
library(multilevelmod)

logistic_reg() %>% 
  set_engine("gee") %>% 
  translate()
```

`multilevelmod::gee_fit()` is a wrapper model around `gee()`. 


## Preprocessing requirements

There are no specific preprocessing needs. However, it is helpful to keep the clustering/subject identifier column as factor or character (instead of making them into dummy variables). See the examples in the next section. 

## Other details

The model cannot accept case weights. 

Both `gee:gee(a)` and `gee:geepack()` specifies the id/cluster variable using an argument `id` that requires a vector. parsnip doesn't work that way so we enable this model to be fit using a artificial function called `id_var()` to be used in the formula. So, in the original package, the call would look like:

```r
gee(breaks ~ tension, id = wool, data = warpbreaks, corstr = "exchangeable")
```

With `parsnip`, we suggest using the formula method when fitting: 

```r
library(tidymodels)
data("toenail", package = "HSAUR3")

logistic_reg() %>% 
  set_engine("gee", corstr = "exchangeable") %>% 
  fit(outcome ~ treatment * visit + id_var(patientID), data = toenail)
```

When using the general tidymodels infrastructure, it may be better to use a workflow. In this case, you can add the appropriate columns using `add_variables()` then supply the GEE formula when adding the model: 

```r
library(tidymodels)

gee_spec <- 
  logistic_reg() %>% 
  set_engine("gee", corstr = "exchangeable")

gee_wflow <- 
  workflow() %>% 
  # The data are included as-is using:
  add_variables(outcomes = outcome, predictors = c(treatment, visit, patientID)) %>% 
  add_model(gee_spec, formula = outcome ~ treatment * visit + id_var(patientID))

fit(gee_wflow, data = toenail)
```

`gee()` always prints out warnings and output even when `silent = TRUE`. When using the `gee` engine, it will never produce output, even if `silent = FALSE`.

Also, because of issues with the `gee()` function, a supplementary call to `glm()` is needed to get the rank and QR decomposition objects so that `predict()` can be used.

## References

 - Liang, K.Y. and Zeger, S.L. (1986) Longitudinal data analysis using generalized linear models. _Biometrika_, 73 13–22.

 - Zeger, S.L. and Liang, K.Y. (1986) Longitudinal data analysis for discrete and continuous outcomes. _Biometrics_, 42 121–130.

