```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("logistic_reg", "keras")`

## Tuning Parameters

```{r}
#| label: keras-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("penalty"),
                 default = c("0.0"))

param <-
  logistic_reg() |> 
  set_engine("keras") |> 
  make_parameter_list(defaults)
```

This model has one tuning parameter:

```{r}
#| label: keras-param-list
#| echo: false
#| results: asis
param$item
```

For `penalty`, the amount of regularization is _only_ L2 penalty (i.e., ridge or weight decay). 

## Translation from parsnip to the original package

```{r}
#| label: keras-csl
logistic_reg(penalty = double(1)) |> 
  set_engine("keras") |> 
  translate()
```

[keras_mlp()] is a parsnip wrapper around keras code for neural networks. This model fits a linear regression as a network with a single hidden unit. 

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-bundle.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#logistic-reg-keras) for `logistic_reg()` with the `"keras"` engine.

## References

 - Hoerl, A., & Kennard, R. (2000). _Ridge Regression: Biased Estimation for Nonorthogonal Problems_. Technometrics, 42(1), 80-86. 

