```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("mars", "earth")`

## Tuning Parameters

```{r earth-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("num_terms", "prod_degree", "prune_method"),
                 default = c("see below", "1L", "'backward'"))

param <-
  mars() %>% 
  set_engine("earth") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r earth-param-list, echo = FALSE, results = "asis"}
param$item
```

The default value of `num_terms` depends on the number of predictor columns. For a data frame `x`, the default is `min(200, max(20, 2 * ncol(x))) + 1` (see [earth::earth()] and the reference below). 

## Translation from parsnip to the original package (regression)

```{r earth-reg}
mars(num_terms = integer(1), prod_degree = integer(1), prune_method = character(1)) %>% 
  set_engine("earth") %>% 
  set_mode("regression") %>% 
  translate()
```

## Translation from parsnip to the original package (classification)

```{r earth-cls}
mars(num_terms = integer(1), prod_degree = integer(1), prune_method = character(1)) %>% 
  set_engine("earth") %>% 
  set_mode("classification") %>% 
  translate()
```

An alternate method for using MARs for categorical outcomes can be found in [discrim_flexible()].


## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

## Case weights

```{r child = "template-uses-case-weights.Rmd"}
```

Note that the `earth` package documentation has: "In the current implementation, _building models with weights can be slow_."

## Saving fitted model objects

```{r child = "template-butcher.Rmd"}
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#mars-earth) for `mars()` with the `"earth"` engine.

## References

 - Friedman, J. 1991. "Multivariate Adaptive Regression Splines." _The Annals of Statistics_, vol. 19, no. 1, pp. 1-67.
 
 - Milborrow, S. ["Notes on the earth package."](http://www.milbo.org/doc/earth-notes.pdf) 
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

