# Engine Details

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below.

## earth

```{r earth-reg}
mars() %>% 
  set_engine("earth") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r earth-cls}
mars() %>% 
  set_engine("earth") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that, when the model is fit, the `earth` package only has its  namespace
loaded. However, if `multi_predict` is used, the package is  attached.


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_mars <- function() {
  tibble::tribble(
    ~model,  ~engine,     ~parsnip,        ~original,  ~default,
    "mars",  "earth",     "prod_degree",   "degree",   get_arg("earth", "earth.fit", "degree"),
    "mars",  "earth",     "prune_method",  "pmethod",  get_arg("earth", "earth.fit", "pmethod")[2]
  )
}
parsnip::convert_args("mars")
```

