# Engine Details

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below:

## keras

```{r keras-reg}
mlp() %>% 
  set_engine("keras") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r keras-cls}
mlp() %>% 
  set_engine("keras") %>% 
  set_mode("classification") %>% 
  translate()
```

An error is thrown if both `penalty` and `dropout` are specified for `keras` models.

## nnet

```{r nnet-reg}
mlp() %>% 
  set_engine("nnet") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r nnet-cls}
mlp() %>% 
  set_engine("nnet") %>% 
  set_mode("classification") %>% 
  translate()
```


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_mlp <- function() {
  tibble::tribble(
    ~model,  ~engine,  ~parsnip,          ~original,       ~default,
    "mlp",   "keras",  "hidden_units",    "hidden_units",  get_arg("parsnip", "keras_mlp", "hidden_units"),
    "mlp",   "keras",  "penalty",         "penalty",       get_arg("parsnip", "keras_mlp", "penalty"),
    "mlp",   "keras",  "dropout",         "dropout",       get_arg("parsnip", "keras_mlp", "dropout"),
    "mlp",   "keras",  "epochs",          "epochs",        get_arg("parsnip", "keras_mlp", "epochs"),
    "mlp",   "keras",  "activation",      "activation",    get_arg("parsnip", "keras_mlp", "activation"),
    "mlp",   "nnet",   "penalty",         "decay",         get_arg("nnet", "nnet.default", "decay"),
    "mlp",   "nnet",   "epochs",          "maxit",         get_arg("nnet", "nnet.default", "maxit"),
  )
}
parsnip::convert_args("mlp")
```

