```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("mlp", "keras")`

## Tuning Parameters

```{r keras-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("hidden_units", "penalty", "dropout", "epochs", "activation"),
                 default = c("5L", "0.0", "0.0", "20L", "'softmax'"))

param <-
  mlp() %>% 
  set_engine("keras") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r keras-param-list, echo = FALSE, results = "asis"}
param$item
```

## Translation from parsnip to the original package (regression)

```{r keras-reg}
mlp(
  hidden_units = integer(1),
  penalty = double(1),
  dropout = double(1),
  epochs = integer(1),
  activation = character(1)
) %>%  
  set_engine("keras") %>% 
  set_mode("regression") %>% 
  translate()
```

## Translation from parsnip to the original package (classification)

```{r keras-cls}
mlp(
  hidden_units = integer(1),
  penalty = double(1),
  dropout = double(1),
  epochs = integer(1),
  activation = character(1)
) %>% 
  set_engine("keras") %>% 
  set_mode("classification") %>% 
  translate()
```


## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

## Case weights

```{r child = "template-no-case-weights.Rmd"}
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#mlp-keras) for `mlp()` with the `"keras"` engine.

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.


