# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below.

## glmnet

```{r glmnet-cls}
multinom_reg() %>% 
  set_engine("glmnet") %>% 
  set_mode("classification") %>% 
  translate()
```

For `glmnet` models, the full regularization path is always fit regardless of the
value given to `penalty`. Also, there is the option to pass  multiple values (or
no values) to the `penalty` argument. When using the  `predict()` method in these
cases, the return value depends on  the value of `penalty`. When using
`predict()`, only a single  value of the penalty can be used. When predicting on
multiple  penalties, the `multi_predict()` function can be used. It  returns a
tibble with a list column called `.pred` that contains  a tibble with all of the
penalty results.

## nnet

```{r nnet-cls}
multinom_reg() %>% 
  set_engine("nnet") %>% 
  set_mode("classification") %>% 
  translate()
```

## spark

```{r spark-cls}
multinom_reg() %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```

## keras

```{r keras-cls}
multinom_reg() %>% 
  set_engine("keras") %>% 
  set_mode("classification") %>% 
  translate()
```


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_multinom_reg <- function() {
  tibble::tribble(
    ~model,          ~engine,     ~parsnip,            ~original,  ~default,
    "multinom_reg",  "glmnet",    "mixture",              "alpha",  get_arg("glmnet", "glmnet", "alpha"),
    "multinom_reg",  "spark",     "penalty",          "reg_param",  get_arg("sparklyr", "ml_logistic_regression", "reg_param"),
    "multinom_reg",  "spark",     "mixture",  "elastic_net_param",  get_arg("sparklyr", "ml_logistic_regression", "elastic_net_param"),
    "multinom_reg",  "keras",     "penalty",            "penalty",  get_arg("parsnip", "keras_mlp", "penalty"),
    "multinom_reg",  "nnet",      "penalty",            "decay",    get_arg("nnet", "nnet.default", "decay"),
  )
}
convert_args("multinom_reg")
```

