# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below.

## glmnet

```{r glmnet-cls}
multinom_reg(penalty = 0.1) %>% 
  set_engine("glmnet") %>% 
  translate()
```

The glmnet engine requires a single value for the `penalty` argument (a number
or `tune()`), but the full regularization path is always fit
regardless of the value given to `penalty`. To pass in a custom sequence of
values for glmnet's `lambda`, use the argument `path_values` in `set_engine()`. 
This will assign the value of the glmnet `lambda` parameter without disturbing
the value given of `multinom_reg(penalty)`. For example: 


```{r glmnet-path}
multinom_reg(penalty = .1) %>% 
  set_engine("glmnet", path_values = c(0, 10^seq(-10, 1, length.out = 20))) %>% 
  translate()
```

When fitting a pure ridge regression model (i.e., `penalty = 0`), we _strongly
suggest_ that you pass in a vector for `path_values` that includes zero. See 
[issue #431](https://github.com/tidymodels/parsnip/issues/431) for a discussion. 

When using `predict()`, the single `penalty` value used for prediction is the 
one specified in `multinom_reg()`. 

To predict on multiple penalties, use the `multi_predict()` function. 
This function returns a tibble with a list column called `.pred` containing 
all of the penalty results.


## nnet

```{r nnet-cls}
multinom_reg() %>% 
  set_engine("nnet") %>% 
  translate()
```

## spark

```{r spark-cls}
multinom_reg() %>% 
  set_engine("spark") %>% 
  translate()
```

## keras

```{r keras-cls}
multinom_reg() %>% 
  set_engine("keras") %>% 
  translate()
```


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_multinom_reg <- function() {
  tibble::tribble(
    ~model,          ~engine,     ~parsnip,            ~original,  ~default,
    "multinom_reg",  "glmnet",    "mixture",              "alpha",  get_arg("glmnet", "glmnet", "alpha"),
    "multinom_reg",  "spark",     "penalty",          "reg_param",  get_arg("sparklyr", "ml_logistic_regression", "reg_param"),
    "multinom_reg",  "spark",     "mixture",  "elastic_net_param",  get_arg("sparklyr", "ml_logistic_regression", "elastic_net_param"),
    "multinom_reg",  "keras",     "penalty",            "penalty",  get_arg("parsnip", "keras_mlp", "penalty"),
    "multinom_reg",  "nnet",      "penalty",            "decay",    get_arg("nnet", "nnet.default", "decay"),
  )
}
convert_args("multinom_reg")
```

