```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("multinom_reg", "spark")`

## Tuning Parameters

```{r}
#| label: spark-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("0.0", "0.0"))

param <-
  multinom_reg() |> 
  set_engine("spark") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: spark-param-list
#| echo: false
#| results: asis
param$item
```

For `penalty`, the amount of regularization includes both the L1 penalty (i.e., lasso) and the L2 penalty (i.e., ridge or weight decay). As for `mixture`:

* `mixture = 1` specifies a pure lasso model,
* `mixture = 0`  specifies a ridge regression model, and
* `0 < mixture < 1` specifies an elastic net model, interpolating lasso and ridge.

## Translation from parsnip to the original package

```{r}
#| label: spark-csl
multinom_reg(penalty = double(1), mixture = double(1)) |> 
  set_engine("spark") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

By default, `ml_multinom_regression()` uses the argument `standardization = TRUE` to center and scale the data. 

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

Note that, for spark engines, the `case_weight` argument value should be a character string to specify the column with the numeric case weights. 


## Other details

```{r}
#| child: template-spark-notes.Rmd
```

## References

 - Luraschi, J, K Kuo, and E Ruiz. 2019. _Mastering Spark with R_. O'Reilly Media
 
 - Hastie, T, R Tibshirani, and M Wainwright. 2015. _Statistical Learning with Sparsity_. CRC Press.
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

