```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("multinom_reg", "nnet")`

## Tuning Parameters

```{r}
#| label: nnet-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("penalty"),
                 default = c("0.0"))

param <-
  multinom_reg() |> 
  set_engine("nnet") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: nnet-param-list
#| echo: false
#| results: asis
param$item
```

For `penalty`, the amount of regularization includes only the L2 penalty (i.e., ridge or weight decay). 

## Translation from parsnip to the original package

```{r}
#| label: nnet-csl
multinom_reg(penalty = double(1)) |> 
  set_engine("nnet") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#multinom-reg-nnet) for `multinom_reg()` with the `"nnet"` engine.

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```

## References

 - Luraschi, J, K Kuo, and E Ruiz. 2019. _Mastering nnet with R_. O'Reilly Media
 
 - Hastie, T, R Tibshirani, and M Wainwright. 2015. _Statistical Learning with Sparsity_. CRC Press.
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

