```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("multinom_reg", "glmnet")`

## Tuning Parameters

```{r glmnet-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("see below", "1.0"))

param <-
multinom_reg() %>% 
  set_engine("glmnet") %>% 
  tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameters:

```{r glmnet-param-list, echo = FALSE, results = "asis"}
param$item
```

A value of `mixture = 1` corresponds to a pure lasso model, while `mixture = 0` indicates ridge regression.

The `penalty` parameter has no default and requires a single numeric value. For more details about this, and the `glmnet` model in general, see [glmnet-details].

## Translation from parsnip to the original package

```{r glmnet-cls}
multinom_reg(penalty = double(1), mixture = double(1)) %>% 
  set_engine("glmnet") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```
By default, [glmnet::glmnet()] uses the argument `standardize = TRUE` to center and scale the data. 

## Example

```{r child = "template-cls-multi-class.Rmd"}
```

We can define the model with specific parameters:

```{r}
mr_cls_spec <- 
  multinom_reg(penalty = 0.1) %>% 
  set_engine("glmnet")
mr_cls_spec
```

Now we create the model fit object:

```{r}
set.seed(1)
mr_cls_fit <- mr_cls_spec %>% fit(island ~ ., data = penguins_train)
mr_cls_fit
```

The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

```{r}
bind_cols(
  predict(mr_cls_fit, penguins_test),
  predict(mr_cls_fit, penguins_test, type = "prob")
)
```

## References

 - Hastie, T, R Tibshirani, and M Wainwright. 2015. _Statistical Learning with Sparsity_. CRC Press.
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

