```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("naive_Bayes", "naivebayes")`

## Tuning Parameters


```{r naivebayes-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("smoothness", "Laplace"),
                 default = c("1.0", "0.0"))

param <-
  naive_Bayes() |> 
  set_engine("naivebayes") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameter:

```{r naivebayes-param-list, echo = FALSE, results = "asis"}
param$item
```

Note that the engine argument `usekernel` is set to `TRUE` by default when using the `naivebayes` engine. 

## Translation from parsnip to the original package

`r uses_extension("naive_Bayes", "naivebayes", "classification")`

```{r naivebayes-cls}
library(discrim)

naive_Bayes(smoothness = numeric(0), Laplace = numeric(0)) |> 
  set_engine("naivebayes") |> 
  translate()
```

## Preprocessing requirements

The columns for qualitative predictors should always be represented as factors (as opposed to dummy/indicator variables). When the predictors are factors, the underlying code treats them as multinomial data and appropriately computes their conditional distributions. 

For count data, integers can be estimated using a Poisson distribution if the argument `usepoisson = TRUE` is passed as an engine argument.  

```{r child = "template-zv.Rmd"}
```

## Case weights

```{r child = "template-no-case-weights.Rmd"}
```

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
