```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("naive_Bayes", "h2o")`

## Tuning Parameters


```{r}
#| label: h2o-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("Laplace"),
                 default = c("0.0"))

param <-
  naive_Bayes() |> 
  set_engine("h2o") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameter:

```{r}
#| label: h2o-param-list
#| echo: false
#| results: asis
param$item
```

[h2o::h2o.naiveBayes()] provides several engine arguments to deal with imbalances and rare classes: 

- `balance_classes` A logical value controlling over/under-sampling (for imbalanced data). Defaults to `FALSE`.

- `class_sampling_factors` The over/under-sampling ratios per class (in lexicographic order). If not specified, sampling factors will be automatically computed to obtain class balance during training. Require `balance_classes` to be `TRUE`.

- `min_sdev`: The minimum standard deviation to use for observations without enough data, must be greater than 1e-10.

- `min_prob`: The minimum probability to use for observations with not enough data.


## Translation from parsnip to the original package

`r uses_extension("naive_Bayes", "h2o", "classification")`

[agua::h2o_train_nb()] is a wrapper around [h2o::h2o.naiveBayes()]. 

```{r}
#| label: h2o-cls
naive_Bayes(Laplace = numeric(0)) |> 
  set_engine("h2o") |> 
  translate()
```

## Initializing h2o 

```{r}
#| child: template-h2o-init.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-bundle.Rmd
```
