# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. For this type of model, the template of the fit calls are below:

## kknn

```{r kknn-reg}
nearest_neighbor() %>% 
  set_engine("kknn") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r kknn-cls}
nearest_neighbor() %>% 
  set_engine("kknn") %>% 
  set_mode("classification") %>% 
  translate()
```

For `kknn`, the underlying modeling function used is a restricted version of
`train.kknn()` and not `kknn()`. It is set up in this way so that `parsnip` can
utilize the underlying `predict.train.kknn` method to predict on new data. This
also means that a single value of that function's `kernel` argument (a.k.a
`weight_func` here) can be supplied

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_nearest_neighbor <- function() {
  tibble::tribble(
    ~model,             ~engine, ~parsnip,        ~original,  ~default,
    "nearest_neighbor", "kknn",  "weight_func",   "kernel",   get_arg("kknn", "train.kknn", "kernel"),
    "nearest_neighbor", "kknn",  "dist_power",    "distance", get_arg("kknn", "train.kknn", "distance"),
  )
}
convert_args("nearest_neighbor")
```

