```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("nearest_neighbor", "kknn")`

## Tuning Parameters

```{r}
#| label: kknn-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("neighbors", "weight_func", "dist_power"),
                 default = c("5L", "'optimal'", "2.0"))

param <-
  nearest_neighbor() |> 
  set_engine("kknn") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: kknn-param-list
#| echo: false
#| results: asis
param$item
```

Parsnip changes the default range for `neighbors` to `c(1, 15)` and `dist_power` to `c(1/10, 2)`.


## Translation from parsnip to the original package (regression)

```{r}
#| label: kknn-reg
nearest_neighbor(
  neighbors = integer(1),
  weight_func = character(1),
  dist_power = double(1)
) |>  
  set_engine("kknn") |> 
  set_mode("regression") |> 
  translate()
```

`min_rows()` will adjust the number of neighbors if the chosen value if it is not consistent with the actual data dimensions.

## Translation from parsnip to the original package (classification)

```{r}
#| label: kknn-cls
nearest_neighbor(
  neighbors = integer(1),
  weight_func = character(1),
  dist_power = double(1)
) |> 
  set_engine("kknn") |> 
  set_mode("classification") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#nearest-neighbor-kknn) for `nearest_neighbor()` with the `"kknn"` engine.

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```

## References

 - Hechenbichler K. and Schliep K.P. (2004) [Weighted k-Nearest-Neighbor Techniques and Ordinal Classification](https://epub.ub.uni-muenchen.de/1769/), Discussion Paper 399, SFB 386, Ludwig-Maximilians University Munich
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
