```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("nearest_neighbor", "kknn")`

## Tuning Parameters

```{r kknn-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("neighbors", "weight_func", "dist_power"),
                 default = c("5L", "'optimal'", "2.0"))

param <-
  nearest_neighbor() %>% 
  set_engine("kknn") %>% 
  tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameters:

```{r kknn-param-list, echo = FALSE, results = "asis"}
param$item
```

## Translation from parsnip to the original package (regression)

```{r kknn-reg}
nearest_neighbor(
  neighbors = integer(1),
  weight_func = character(1),
  dist_power = double(1)
) %>%  
  set_engine("kknn") %>% 
  set_mode("regression") %>% 
  translate()
```

`min_rows()` will adjust the number of neighbors if the chosen value if it is not consistent with the actual data dimensions.

## Translation from parsnip to the original package (classification)

```{r kknn-cls}
nearest_neighbor(
  neighbors = integer(1),
  weight_func = character(1),
  dist_power = double(1)
) %>% 
  set_engine("kknn") %>% 
  set_mode("classification") %>% 
  translate()
```


## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

## Examples

```{r child = "template-reg-chicago.Rmd"}
```

We can define the model with specific parameters:

```{r}
knn_reg_spec <- 
  nearest_neighbor(neighbors = 5, weight_func = "triangular") %>% 
  # This model can be used for classification or regression, so set mode
  set_mode("regression") %>% 
  set_engine("kknn")
knn_reg_spec
```

Now we create the model fit object:

```{r}
knn_reg_fit <- knn_reg_spec %>% fit(ridership ~ ., data = Chicago_train)
knn_reg_fit
```

The holdout data can be predicted:

```{r}
predict(knn_reg_fit, Chicago_test)
```


```{r child = "template-cls-two-class.Rmd"}
```

Since there are two classes, we'll use an odd number of neighbors to avoid ties: 

```{r}
knn_cls_spec <- 
  nearest_neighbor(neighbors = 11, weight_func = "triangular") %>% 
  # This model can be used for classification or regression, so set mode
  set_mode("classification") %>% 
  set_engine("kknn")
knn_cls_spec
```

Now we create the model fit object:

```{r}
knn_cls_fit <- knn_cls_spec %>% fit(Class ~ ., data = data_train)
knn_cls_fit
```

The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

```{r}
bind_cols(
  predict(knn_cls_fit, data_test),
  predict(knn_cls_fit, data_test, type = "prob")
)
```



## References

 - Hechenbichler K. and Schliep K.P. (2004) [Weighted k-Nearest-Neighbor Techniques and Ordinal Classification](https://epub.ub.uni-muenchen.de/1769/), Discussion Paper 399, SFB 386, Ludwig-Maximilians University Munich
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
