```{r load, include = FALSE}
library(dplyr)
```

By default, `model.matrix()` generates binary indicator variables for all but one of the levels for factor predictors when the formula does not remove an intercept. 

For example, `species` and `island` both have three levels:

```{r ref-cell}
library(dplyr)
library(modeldata)
data(penguins)

model.matrix(~ species + island, data = penguins) %>% 
  colnames()
```

When there is no intercept, the first factor receives indicators for _all_ factor levels but all other factors get all but one (as above):

```{r hybrid}
model.matrix(~ 0 + species + island, data = penguins) %>% 
  colnames()
```

For inference, this hybrid encoding can be problematic. 

To generate all indicators, this contrast can be used: 

```{r one-hot}
# Switch out the contrast method
old_contr <- options("contrasts")$contrasts
new_contr <- old_contr
new_contr["unordered"] <- "contr_one_hot"
options(contrasts = new_contr)

model.matrix(~ species + island, data = penguins) %>% 
  colnames()

options(contrasts = old_contr)
```

Removing the intercept here does not affect the factor encodings. 

 
