```{r, child="aaa.Rmd", include=FALSE}
```

`r descr_models("ordinal_reg", "ordinalNet")`

## Tuning Parameters

```{r ordinalNet-param-info, echo=FALSE}
defaults <- 
  tibble::tibble(
    parsnip = c("ordinal_link", "odds_link", "penalty", "mixture"),
    default = c("logit", "cumulative", "see below", "1.0")
  )

param <-
  ordinal_reg() |>
  set_engine("ordinalNet") |>
  set_mode("classification") |>
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r, ordinalNet-param-list, echo=FALSE, results='asis'}
param$item
```

## Translation from parsnip to the original package

`r uses_extension("ordinal_reg", "ordinalNet", "classification")`

```{r ordinalNet-oreg, warning = FALSE}
library(ordered)

ordinal_reg(
  penalty = double(0),
  mixture = double(0),
  ordinal_link = character(0),
  odds_link = character(0)
) %>%
  set_engine("ordinalNet") %>%
  set_mode("classification") %>%
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

By default, [ordinalNet::ordinalNet()] uses the argument `standardize = TRUE` to center and scale the data. 

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types
parsnip:::get_from_env("ordinal_reg_predict") |>
  dplyr::filter(engine == "ordinalNet") |>
  dplyr::select(mode, type)
```

## References

- Wurm MJ, Rathouz PJ, Hanlon BM. 2021. Regularized Ordinal Regression and the ordinalNet R Package. _Journal of Statistical Software_ 99(6):1-42. \doi{10.18637/jss.v099.i06}.
