```{r, child="aaa.Rmd", include=FALSE}
```

`r descr_models("ordinal_reg", "vglm")`

## Tuning Parameters

```{r vglm-param-info, echo=FALSE}
defaults <- 
  tibble::tibble(
    parsnip = c("ordinal_link", "odds_link"),
    default = c("logit", "cumulative")
  )

param <-
  ordinal_reg() |>
  set_engine("ordinalNet") |>
  set_mode("classification") |>
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r, vglm-param-list, echo=FALSE, results='asis'}
param$item
```

## Translation from parsnip to the original package

`r uses_extension("ordinal_reg", "vglm", "classification")`

```{r vglm-oreg}
library(ordered)

ordinal_reg(ordinal_link = character(0), odds_link = character(0)) %>% 
  set_engine("vglm") %>% 
  set_mode("classification") %>% 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

_However_, the documentation in [VGAM::vglm()] notes that matrix of case weights can be passed so that different classes have different weights. tidymodels assumes vector of a weights; a matrix cannot be passed in. 

Also, the engine documentation notes that: "The values of weights must be positive; try setting a very small value such as 1.0e-8 to effectively delete an observation."

## Prediction types

```{r}
#| label: predict-types
parsnip:::get_from_env("ordinal_reg_predict") |>
  dplyr::filter(engine == "vglm") |>
  dplyr::select(mode, type)
```



## References

- Yee T. 2010. The VGAM Package for Categorical Data Analysis. _Journal of Statistical Software_ 32(10):1--34. \doi{10.18637/jss.v032.i10}.
