```{r, child="aaa.Rmd", include=FALSE}
```

`r descr_models("ordinal_reg", "ordinalNet")`

## Tuning Parameters

```{r ordinalNet-param-info, echo=FALSE}
defaults <- 
  tibble::tibble(
    parsnip = c("ordinal_link", "odds_link", "penalty", "mixture"),
    default = c("logit", "cumulative", "see below", "1.0")
  )

param <-
  ordinal_reg() |>
  set_engine("ordinalNet") |>
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r, ordinalNet-param-list, echo=FALSE, results='asis'}
param$item
```

## Translation from parsnip to the original package

`r uses_extension("ordinal_reg", "ordinalNet", "classification")`

```{r ordinalNet-oreg, warning = FALSE}
library(ordered)

ordinal_reg(
  penalty = double(0),
  mixture = double(0),
  ordinal_link = character(0),
  odds_link = character(0)
) %>%
  set_engine("ordinalNet") %>%
  # "classification" is the only mode
  translate()
```

## Controlling penalty values

`ordinalNet()`, like `glmnet()`, simultaneously computes a set of parameter estimates for multiple penalty values. Predictions can be made at these penalty values at the same time. However, unlike `glmnet()`, `ordinalNet()` does not interpolate if you want to predict a penalty values that is not exactly what it precomputed. Similarly, it cannot predict for models outside of the range of penalties. 

The \pkg{ordered} package can interpolate between the preset penalty values but cannot predict outside of their range and this will cause an error. 

We suggest that you set the collection of penalty values when fitting the model. This is important when tuning the model. Different data sets and mixture values (a.k.a. `alpha`) will have different sets of penalties and it might be good to set a wide range. 

To do this, you can use `set_engine()` to pass a vector of penalty values as so: 

```r
# Example of setting a wide penalty range
penalties <- 10^seq(-10, 0, length.out = 20)

ordinal_reg(penalty = tune()) |>
  set_engine("ordinalNet", path_values = !!penalties)
```

See [`glmnet-details`] for more background. 

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

By default, [ordinalNet::ordinalNet()] uses the argument `standardize = TRUE` to center and scale the data. 

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types
parsnip:::get_from_env("ordinal_reg_predict") |>
  dplyr::filter(engine == "ordinalNet") |>
  dplyr::select(mode, type)
```

## References

- Wurm MJ, Rathouz PJ, Hanlon BM. 2021. Regularized Ordinal Regression and the ordinalNet R Package. _Journal of Statistical Software_ 99(6):1-42. \doi{10.18637/jss.v099.i06}.
