```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("pls", "mixOmics")`

## Tuning Parameters

```{r mixOmics-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("num_comp", "predictor_prop"),
                 default = c("2L",           "see below"))

param <-
  pls() |> 
  set_engine("mixOmics") |> 
  set_mode("regression") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r mixOmics-param-list, echo = FALSE, results = "asis"}
param$item
```


## Translation from parsnip to the underlying model call  (regression)

`r uses_extension("pls", "mixOmics", "regression")`

```{r mixOmics-reg}
library(plsmod)

pls(num_comp = integer(1), predictor_prop = double(1)) |>
  set_engine("mixOmics") |>
  set_mode("regression") |>
  translate()
```

[plsmod::pls_fit()] is a function that: 

 - Determines the number of predictors in the data.
 - Adjusts `num_comp` if the value is larger than the number of factors.
 - Determines whether sparsity is required based on the value of `predictor_prop`.
 - Sets the `keepX` argument of `mixOmics::spls()` for sparse models. 

## Translation from parsnip to the underlying model call  (classification)

`r uses_extension("pls", "mixOmics", "classification")`

```{r mixOmics-cls}
library(plsmod)

pls(num_comp = integer(1), predictor_prop = double(1)) |>
  set_engine("mixOmics") |>
  set_mode("classification") |>
  translate()
```

In this case, [plsmod::pls_fit()] has the same role as above but eventually targets `mixOmics::plsda()` or `mixOmics::splsda()`.

## Installing mixOmics

This package is available via the Bioconductor repository and is not accessible via CRAN. You can install using: 

```{r eval = FALSE}
  if (!require("remotes", quietly = TRUE)) {
    install.packages("remotes")
  }
  
  remotes::install_bioc("mixOmics")
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-zv.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

## Case weights

```{r child = "template-no-case-weights.Rmd"}
```

## References

 - Rohart F and Gautier B and Singh A and Le Cao K-A  (2017). "mixOmics: An R package for 'omics feature selection and multiple data integration." PLoS computational biology, 13(11), e1005752.
 
