```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("poisson_reg", "h2o")`

## Tuning Parameters

```{r}
#| label: h2o-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("see below", "see below"))

param <-
poisson_reg() |> 
  set_engine("h2o") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: h2o-param-list
#| echo: false
#| results: asis
param$item
```

```{r}
#| child: template-h2o-glm-penalty.Rmd
#| include: false
```

## Translation from parsnip to the original package

[agua::h2o_train_glm()] for `poisson_reg()` is a wrapper around [h2o::h2o.glm()] with `family = 'poisson'`. 

`r uses_extension("poisson_reg", "h2o", "regression")`

```{r}
#| label: h2o-csl
library(poissonreg)

poisson_reg(penalty = double(1), mixture = double(1)) |> 
  set_engine("h2o") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

By default, `h2o::h2o.glm()` uses the argument `standardize = TRUE` to center and scale all numerical columns. 


## Initializing h2o  

```{r}
#| child: template-h2o-init.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-bundle.Rmd
```
