```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("poisson_reg", "glmnet")`

## Tuning Parameters

```{r glmnet-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("penalty", "mixture"),
                 default = c("see below", "1.0"))

param <-
poisson_reg() %>% 
  set_engine("glmnet") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r glmnet-param-list, echo = FALSE, results = "asis"}
param$item
```

A value of `mixture = 1` corresponds to a pure lasso model, while `mixture = 0` indicates ridge regression.

The `penalty` parameter has no default and requires a single numeric value. For more details about this, and the `glmnet` model in general, see [glmnet-details].

## Translation from parsnip to the original package

`r uses_extension("poisson_reg", "glmnet", "regression")`

```{r glmnet-csl}
library(poissonreg)

poisson_reg(penalty = double(1), mixture = double(1)) %>% 
  set_engine("glmnet") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```
By default, `glmnet::glmnet()` uses the argument `standardize = TRUE` to center and scale the data. 


## Case weights

```{r child = "template-uses-case-weights.Rmd"}
```
