```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("poisson_reg", "glm")`

## Tuning Parameters

This engine has no tuning parameters. 

## Translation from parsnip to the underlying model call  (regression)

`r uses_extension("poisson_reg", "glm", "regression")`

```{r}
#| label: glm-reg
library(poissonreg)

poisson_reg() |>
  set_engine("glm") |>
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```


## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

_However_, the documentation in [stats::glm()] assumes that is specific type of case weights are being used:"Non-NULL weights can be used to indicate that different observations have different dispersions (with the values in weights being inversely proportional to the dispersions); or equivalently, when the elements of weights are positive integers `w_i`, that each response `y_i` is the mean of `w_i` unit-weight observations. For a binomial GLM prior weights are used to give the number of trials when the response is the proportion of successes: they would rarely be used for a Poisson GLM."

If frequency weights are being used in your application, the [glm_grouped()] model (and corresponding engine) may be more appropriate. 

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```
