```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("poisson_reg", "hurdle")`

## Tuning Parameters

This engine has no tuning parameters. 

## Translation from parsnip to the underlying model call  (regression)

`r uses_extension("poisson_reg", "hurdle", "regression")`

```{r}
#| label: hurdle-reg
library(poissonreg)

poisson_reg() |>
  set_engine("hurdle") |>
  translate()
```

## Preprocessing and special formulas for zero-inflated Poisson models

```{r}
#| child: template-makes-dummies.Rmd
```

## Specifying the statistical model details

For this particular model, a special formula is used to specify which columns affect the counts and which affect the model for the probability of zero counts. These sets of terms are separated by a bar. For example, `y ~ x | z`. This type of formula is not used by the base R infrastructure (e.g. `model.matrix()`)

When fitting a parsnip model with this engine directly, the formula method is required and the formula is just passed through. For example:

```{r}
#| include: false
library(tidymodels)
```

```{r}
#| message: false
library(tidymodels)
tidymodels_prefer()

data("bioChemists", package = "pscl")
poisson_reg() |> 
  set_engine("hurdle") |> 
  fit(art ~ fem + mar | ment, data = bioChemists)
```

However, when using a workflow, the best approach is to avoid using [workflows::add_formula()] and use [workflows::add_variables()] in conjunction with a model formula:

```{r}
data("bioChemists", package = "pscl")
spec <- 
  poisson_reg() |> 
  set_engine("hurdle")

workflow() |> 
  add_variables(outcomes = c(art), predictors = c(fem, mar, ment)) |> 
  add_model(spec, formula = art ~ fem + mar | ment) |> 
  fit(data = bioChemists) |> 
  extract_fit_engine()
```

The reason for this is that [workflows::add_formula()] will try to create the model matrix and either fail or create dummy variables prematurely. 

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```
