```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("poisson_reg", "stan")`

## Tuning Parameters

This engine has no tuning parameters.

## Important engine-specific options

Some relevant arguments that can be passed to `set_engine()`: 

 * `chains`: A positive integer specifying the number of Markov chains. The default is 4.
 * `iter`: A positive integer specifying the number of iterations for each chain (including warmup). The default is 2000.
 * `seed`: The seed for random number generation. 
 * `cores`: Number of cores to use when executing the chains in parallel.
 * `prior`: The prior distribution for the (non-hierarchical) regression coefficients. The `"stan"` engine does not fit any hierarchical terms. 
 * `prior_intercept`: The prior distribution for the intercept (after centering all predictors). 
 
See [rstan::sampling()] and [rstanarm::priors()] for more information on these and other options.  

## Translation from parsnip to the original package

`r uses_extension("poisson_reg", "stan", "regression")`

```{r}
#| label: stan-csl
library(poissonreg)

poisson_reg() |> 
  set_engine("stan") |> 
  translate()
```

Note that the `refresh` default prevents logging of the estimation process. Change this value in `set_engine()` to show the MCMC logs.

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Other details

For prediction, the `"stan"` engine can compute posterior intervals analogous to confidence and prediction intervals. In these instances, the units are the original outcome. When `std_error = TRUE`, the standard deviation of the posterior  distribution (or posterior predictive distribution as  appropriate) is returned.

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#linear-reg-stan) for `poisson_reg()` with the `"stan"` engine.

## References

 - McElreath, R. 2020 _Statistical Rethinking_. CRC Press.
