```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("proportional_hazards", "survival")`

## Tuning Parameters

This model has no tuning parameters.

## Translation from parsnip to the original package

`r uses_extension("proportional_hazards", "survival", "censored regression")`

```{r}
#| label: survival-creg
library(censored)

proportional_hazards() |> 
  set_engine("survival") |> 
  set_mode("censored regression") |> 
  translate()
```

## Other details

The model does not fit an intercept. 

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

The model formula can include _special_ terms, such as [survival::strata()]. The allows the baseline hazard to differ between groups contained in the function. The column used inside `strata()` is treated as qualitative no matter its type. To learn more about using special terms in formulas with tidymodels, see [`?model_formula`][parsnip::model_formula].

For example, in this model, the numeric column `rx` is used to estimate two different baseline hazards for each value of the column:

```{r}
library(survival)

proportional_hazards() |> 
  fit(Surv(futime, fustat) ~ age + strata(rx), data = ovarian) |> 
  extract_fit_engine() |> 
  # Two different hazards for each value of 'rx'
  basehaz()
```

Note that columns used in the `strata()` function will not be estimated in the regular portion of the model (i.e., within the linear predictor).

```{r}
#| child: template-survival-mean.Rmd
```

## Linear predictor values

```{r}
#| child: template-censored-linear-predictor.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## References

- Andersen P, Gill R. 1982. Cox's regression model for counting processes, a large sample study. _Annals of Statistics_ 10, 1100-1120.
