# Engine Details

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below:

## ranger

```{r ranger-reg}
rand_forest() %>% 
  set_engine("ranger") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r ranger-cls}
rand_forest() %>% 
  set_engine("ranger") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [ranger::ranger()] does not require factor predictors to be converted 
to indicator variables. 

For `ranger` confidence intervals, the intervals are  constructed using the form
`estimate +/- z * std_error`. For  classification probabilities, these values can
fall outside of  `[0, 1]` and will be coerced to be in this range.

## randomForest

```{r randomForest-reg}
rand_forest() %>% 
  set_engine("randomForest") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r randomForest-cls}
rand_forest() %>% 
  set_engine("randomForest") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [randomForest::randomForest()] does not require factor predictors to be converted 
to indicator variables. 

## spark

```{r spark-reg}
rand_forest() %>% 
  set_engine("spark") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r spark-cls}
rand_forest() %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```


## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters:

```{r echo = FALSE, results = "asis"}
parsnip::convert_args("rand_forest")
```

