```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("rand_forest", "party")`

## Tuning Parameters

```{r party-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("trees", "min_n", "mtry"),
                 default = c("500L", "20L", "5L"))

param <-
  rand_forest() %>% 
  set_engine("party") %>% 
  set_mode("censored regression") %>%  
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r party-param-list, echo = FALSE, results = "asis"}
param$item
```

## Translation from parsnip to the original package (censored regression)

```{r party-creg}
rand_forest() %>% 
  set_engine("party") %>% 
  set_mode("censored regression") %>% 
  translate()
```

[cond_inference_surv_cforest()] is a wrapper around [party::cforest()] (and other functions) that makes it easier to run this model. 

## Preprocessing requirements

```{r child = "template-tree-split-factors.Rmd"}
```

## Other details

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 


## References

 - Hothorn T, Buhlmann P, Dudoit S, Molinaro A, Van der Laan MJ. 2006. Survival Ensembles. _Biostatistics_, 7(3), 355–373.

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
