# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below:

## ranger

```{r ranger-reg}
rand_forest() %>% 
  set_engine("ranger") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r ranger-cls}
rand_forest() %>% 
  set_engine("ranger") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [ranger::ranger()] does not require factor predictors to be converted  to indicator variables. `fit()` does not affect the encoding of the predictor values (i.e. factors stay factors) for this model.

For `ranger` confidence intervals, the intervals are  constructed using the form
`estimate +/- z * std_error`. For  classification probabilities, these values can
fall outside of  `[0, 1]` and will be coerced to be in this range.

## randomForest

```{r randomForest-reg}
rand_forest() %>% 
  set_engine("randomForest") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r randomForest-cls}
rand_forest() %>% 
  set_engine("randomForest") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that [randomForest::randomForest()] does not require factor predictors to be converted  to indicator variables. `fit()` does not affect the encoding of the predictor values (i.e. factors stay factors) for this model.

## spark

```{r spark-reg}
rand_forest() %>% 
  set_engine("spark") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r spark-cls}
rand_forest() %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```

`fit()` does not affect the encoding of the predictor values (i.e. factors stay factors) for this model.

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
get_defaults_rand_forest <- function() {
  tibble::tribble(
    ~model,         ~engine,          ~parsnip,   ~original,                  ~default,
    "rand_forest",  "ranger",         "trees",    "num.trees",                get_arg("ranger", "ranger", "num.trees"),
    "rand_forest",  "ranger",         "mtry",     "mtry",                     "see below",
    "rand_forest",  "ranger",         "min_n",    "min.node.size",            "see below",
    "rand_forest",  "randomForest",   "trees",    "ntree",                    get_arg("randomForest", "randomForest.default", "ntree"),
    "rand_forest",  "randomForest",   "mtry",     "mtry",                     "see below",
    "rand_forest",  "randomForest",   "min_n",    "nodesize",                 "see below",
    "rand_forest",  "spark",          "trees",    "num_trees",                get_arg("sparklyr", "ml_random_forest", "num_trees"),
    "rand_forest",  "spark",          "mtry",     "feature_subset_strategy",  "see below",
    "rand_forest",  "spark",          "min_n",    "min_instances_per_node",   get_arg("sparklyr", "ml_random_forest", "min_instances_per_node"),
  )
}
convert_args("rand_forest")
```

- For randomForest and spark, the default `mtry` is the square root of the number of predictors for classification, and one-third of the predictors for regression.
- For ranger, the default `mtry` is the square root of the number of predictors.
- The default `min_n` for both ranger and randomForest is 1 for classification and 5 for regression.
