```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("rand_forest", "ranger")`

## Tuning Parameters

```{r}
#| label: ranger-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("mtry", "trees", "min_n"),
                 default = c("see below", "500L", "see below"))

param <-
  rand_forest() |> 
  set_engine("ranger") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: ranger-param-list
#| echo: false
#| results: asis
param$item
```

`mtry` depends on the number of columns. The default in [ranger::ranger()] is `floor(sqrt(ncol(x)))`.

`min_n` depends on the mode. For regression, a value of 5 is the default. For classification, a value of 10 is used. 

## Translation from parsnip to the original package (regression)

```{r}
#| label: ranger-reg
rand_forest(
  mtry = integer(1),
  trees = integer(1),
  min_n = integer(1)
) |>  
  set_engine("ranger") |> 
  set_mode("regression") |> 
  translate()
```

`min_rows()` and `min_cols()` will adjust the number of neighbors if the chosen value if it is not consistent with the actual data dimensions.

## Translation from parsnip to the original package (classification)

```{r}
#| label: ranger-cls
rand_forest(
  mtry = integer(1),
  trees = integer(1),
  min_n = integer(1)
) |> 
  set_engine("ranger") |> 
  set_mode("classification") |> 
  translate()
```

Note that a `ranger` probability forest is always fit (unless the `probability` argument is changed by the user via [set_engine()]).

## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```

## Other notes

By default, parallel processing is turned off. When tuning, it is more efficient to parallelize over the resamples and tuning parameters. To parallelize the construction of the trees within the `ranger` model, change the `num.threads` argument via [set_engine()]. 

For `ranger` confidence intervals, the intervals are  constructed using the form `estimate +/- z * std_error`. For  classification probabilities, these values can fall outside of  `[0, 1]` and will be coerced to be in this range.

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Sparse Data

```{r}
#| child: template-uses-sparse-data.Rmd
```

While this engine supports sparse data as an input, it doesn't use it any differently than dense data. Hence there it no reason to convert back and forth.

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```


## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#rand-forest-ranger) for `rand_forest()` with the `"ranger"` engine.

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
