```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("rand_forest", "partykit")`

## Tuning Parameters

```{r}
#| label: partykit-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("trees", "min_n", "mtry"),
                 default = c("500L", "20L", "5L"))

param <-
  rand_forest() |> 
  set_engine("partykit") |> 
  set_mode("regression") |>  
  make_parameter_list(defaults) |> 
  distinct()
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: partykit-param-list
#| echo: false
#| results: asis
param$item
```

## Translation from parsnip to the original package (regression)

`r uses_extension("rand_forest", "partykit", "regression")`

```{r}
#| label: partykit-creg
library(bonsai)

rand_forest() |> 
  set_engine("partykit") |> 
  set_mode("regression") |> 
  translate()
```

## Translation from parsnip to the original package (classification)

`r uses_extension("rand_forest", "partykit", "classification")`

```{r}
#| label: partykit-class
library(bonsai)

rand_forest() |> 
  set_engine("partykit") |> 
  set_mode("classification") |> 
  translate()
```

`parsnip::cforest_train()` is a wrapper around [partykit::cforest()] (and other functions) that makes it easier to run this model. 

# Translation from parsnip to the original package (censored regression)

`r uses_extension("rand_forest", "partykit", "censored regression")`

```{r}
#| label: party-creg
library(censored)

rand_forest() |> 
  set_engine("partykit") |> 
  set_mode("censored regression") |> 
  translate()
```

`censored::cond_inference_surv_cforest()` is a wrapper around [partykit::cforest()] (and other functions) that makes it easier to run this model. 


## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("rand_forest_predict") |>
  dplyr::filter(engine == "partykit") |>
  dplyr::select(mode, type)

```

## Other details

```{r}
#| child: template-survival-median.Rmd
```

## References

 - [partykit: A Modular Toolkit for Recursive Partytioning in R](https://jmlr.org/papers/v16/hothorn15a.html)

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
