```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("rand_forest", "h2o")`

## Tuning Parameters

```{r}
#| label: h2o-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("mtry", "trees", "min_n"),
                 default = c("see below", "50L", 1))

param <-
  rand_forest() |> 
  set_engine("h2o") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: h2o-param-list
#| echo: false
#| results: asis
param$item
```

`mtry` depends on the number of columns and the model mode. The default in [h2o::h2o.randomForest()] is `floor(sqrt(ncol(x)))` for classification and `floor(ncol(x)/3)` for regression.

## Translation from parsnip to the original package (regression)

[agua::h2o_train_rf()] is a wrapper around [h2o::h2o.randomForest()]. 

```{r}
#| label: h2o-reg
rand_forest(
  mtry = integer(1),
  trees = integer(1),
  min_n = integer(1)
) |>  
  set_engine("h2o") |> 
  set_mode("regression") |> 
  translate()
```

`min_rows()` and `min_cols()` will adjust the number of neighbors if the chosen value if it is not consistent with the actual data dimensions.

## Translation from parsnip to the original package (classification)

```{r}
#| label: h2o-cls
rand_forest(
  mtry = integer(1),
  trees = integer(1),
  min_n = integer(1)
) |> 
  set_engine("h2o") |> 
  set_mode("classification") |> 
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```


## Initializing h2o 

```{r}
#| child: template-h2o-init.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-bundle.Rmd
```
