```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("rand_forest", "randomForestSRC")`

## Tuning Parameters

```{r}
#| label: randomForestSRC-param-info
#| echo: false
defaults <-
  tibble::tibble(
    parsnip = c("trees", "min_n", "mtry"),
    default = c("500L", "15L", "ceiling(sqrt(n_predictors))")
  )

param <-
  rand_forest() |>
  set_engine("randomForestSRC") |>
  set_mode("censored regression") |>
  make_parameter_list(defaults) |>
  distinct()
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: randomForestSRC-param-list
#| echo: false
#| results: asis
param$item
```

## Translation from parsnip to the original package (censored regression)

`r uses_extension("rand_forest", "randomForestSRC", "censored regression")`

```{r}
#| label: randomForestSRC-creg
library(censored)

rand_forest() |>
  set_engine("randomForestSRC") |>
  set_mode("censored regression") |>
  translate()
```

`censored::rfsrc_train()` is a wrapper around [randomForestSRC::rfsrc()] that makes it easier to run this model.

## Preprocessing requirements

```{r}
#| child: template-tree-split-factors.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("rand_forest_predict") |>
  dplyr::filter(engine == "randomForestSRC") |>
  dplyr::select(mode, type) |>
  print(n = Inf)
```

## Other details

```{r}
#| child: template-survival-median.Rmd
```

## References

- Ishwaran H, Kogalur UB, Blackstone EH, Lauer MS. Random survival forests. Annals of Applied Statistics 2008; 2(3):841-860. \doi{10.1214/08-AOAS169}.
