```{r, child="aaa.Rmd", include=FALSE}
```

`r descr_models("rand_forest", "ordinalForest")`

## Tuning Parameters

```{r}
#| label: ordinalForest-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("mtry", "trees", "min_n"),
                 default = c("see below", "500L", "see below"))

param <-
  rand_forest() |> 
  set_engine("ordinalForest") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r ordinalForest-param-list, echo=FALSE, results='asis'}
param$item
```

`mtry` depends on the number of columns and the model mode. The default in [ordinalForest::ordfor()] is `floor(sqrt(ncol(x)))`.

`min_n` depends on the mode. For regression, a value of 5 is the default. For classification, a value of 10 is used. 

## Translation from parsnip to the original package (classification)

```{r, ordinalForest-cls}
rand_forest(
  mtry = integer(1),
  trees = integer(1),
  min_n = integer(1)
) |> 
  set_engine("ordinalForest") |> 
  set_mode("classification") |> 
  translate()
```

<!--
REVIEW: Add any needed sections here.
-->

## References

- Hornung R. 2020. Ordinal Forests. _Journal of Classification_ 37:4-17. \doi{10.1007/s00357-018-9302-x}.

- Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.
