```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("rand_forest", "spark")`

## Tuning Parameters

```{r spark-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("mtry", "trees", "min_n"),
                 default = c("see below", "20L", "1L"))

param <-
  rand_forest() %>% 
  set_engine("spark") %>% 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r spark-param-list, echo = FALSE, results = "asis"}
param$item
```

`mtry` depends on the number of columns and the model mode. The default in [sparklyr::ml_random_forest()] is `floor(sqrt(ncol(x)))` for classification and `floor(ncol(x)/3)` for regression.

## Translation from parsnip to the original package (regression)

```{r spark-reg}
rand_forest(
  mtry = integer(1),
  trees = integer(1),
  min_n = integer(1)
) %>%  
  set_engine("spark") %>% 
  set_mode("regression") %>% 
  translate()
```

`min_rows()` and `min_cols()` will adjust the number of neighbors if the chosen value if it is not consistent with the actual data dimensions.

## Translation from parsnip to the original package (classification)

```{r spark-cls}
rand_forest(
  mtry = integer(1),
  trees = integer(1),
  min_n = integer(1)
) %>% 
  set_engine("spark") %>% 
  set_mode("classification") %>% 
  translate()
```

## Preprocessing requirements

```{r child = "template-tree-split-factors.Rmd"}
```

## Other details

```{r child = "template-spark-notes.Rmd"}
```

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

