```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("rand_forest", "aorsf")`

## Tuning Parameters

```{r aorsf-param-info, echo = FALSE}
defaults <-
  tibble::tibble(parsnip = c("trees", "min_n", "mtry"),
                 default = c("500L", "5L", "ceiling(sqrt(n_predictors))"))

param <-
  rand_forest() %>%
  set_engine("aorsf") %>%
  set_mode("censored regression") %>%
  make_parameter_list(defaults) %>%
  distinct()
```

This model has `r nrow(param)` tuning parameters:

```{r aorsf-param-list, echo = FALSE, results = "asis"}
param$item
```

Additionally, this model has one engine-specific tuning parameter:

 * `split_min_stat`: Minimum test statistic required to split a node. Default is `3.841459` for the log-rank test, which is roughly a p-value of 0.05.


# Translation from parsnip to the original package (censored regression)

`r uses_extension("rand_forest", "aorsf", "censored regression")`

```{r aorsf-creg}
library(censored)

rand_forest() %>%
  set_engine("aorsf") %>%
  set_mode("censored regression") %>%
  translate()
```

## Preprocessing requirements

```{r child = "template-tree-split-factors.Rmd"}
```

## Case weights

```{r child = "template-uses-case-weights.Rmd"}
```

## Other details

Predictions of survival probability at a time exceeding the maximum observed event time are the predicted survival probability at the maximum observed time in the training data.

## References

- Jaeger BC, Long DL, Long DM, Sims M, Szychowski JM, Min YI, Mcclure LA, Howard G, Simon N. Oblique random survival forests. Annals of applied statistics 2019 Sep; 13(3):1847-83. DOI: 10.1214/19-AOAS1261

- Jaeger BC, Welden S, Lenoir K, Pajewski NM. aorsf: An R package for supervised learning using the oblique random survival forest. Journal of Open Source Software 2022, 7(77), 1 4705. https://doi.org/10.21105/joss.04705.

- Jaeger BC, Welden S, Lenoir K, Speiser JL, Segar MW, Pandey A, Pajewski NM. Accelerated and interpretable oblique random survival forests. arXiv e-prints 2022 Aug; arXiv-2208. URL: https://arxiv.org/abs/2208.01129
