```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("rule_fit", "h2o")`

## Tuning Parameters

```{r}
#| label: h2o-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("tree_depth", "trees", "penalty"),
                 default = c("3L", "50L", 0))

param <-
  rule_fit() |> 
  set_engine("h2o") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: h2o-param-list
#| echo: false
#| results: asis
param$item
```
Note that `penalty` for the h2o engine in `rule_fit()`` corresponds to the L1 penalty (LASSO). 


Other engine arguments of interest: 

- `algorithm`: The algorithm to use to generate rules. should be one of "AUTO", "DRF", "GBM", defaults to "AUTO".

- `min_rule_length`: Minimum length of tree depth, opposite of `tree_dpeth`, defaults to 3.

- `max_num_rules`: The maximum number of rules to return. The default value of -1 means the number of rules is selected by diminishing returns in model deviance. 

- `model_type`: The type of base learners in the ensemble, should be one of: "rules_and_linear", "rules", "linear", defaults to "rules_and_linear".


## Translation from parsnip to the underlying model call  (regression)

[agua::h2o_train_rule()] is a wrapper around [h2o::h2o.rulefit()]. 

`r uses_extension("rule_fit", "h2o", "regression")`

```{r}
#| label: h2o-reg
library(rules)

rule_fit(
  trees = integer(1),
  tree_depth = integer(1),
  penalty = numeric(1)
) |>
  set_engine("h2o") |>
  set_mode("regression") |>
  translate()
```

## Translation from parsnip to the underlying model call  (classification)



[agua::h2o_train_rule()] for `rule_fit()` is a wrapper around [h2o::h2o.rulefit()]. 

`r uses_extension("rule_fit", "h2o", "classification")`

```{r}
#| label: h2o-cls
rule_fit(
  trees = integer(1),
  tree_depth = integer(1),
  penalty = numeric(1)
) |>
  set_engine("h2o") |>
  set_mode("classification") |>
  translate()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Other details

```{r}
#| child: template-h2o-init.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-bundle.Rmd
```
