```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("surv_reg", "survival")`

## Tuning Parameters

```{r survival-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("dist"),
                 default = c("'weibull'"))

param <-
  surv_reg() %>%
  set_engine("survival") %>%
  set_mode("regression") %>%
    make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r survival-param-list, echo = FALSE, results = "asis"}
param$item
```

## Translation from parsnip to the original package

```{r survival-reg, warning = FALSE}
surv_reg(dist = character(1)) %>% 
  set_engine("survival") %>% 
  set_mode("regression") %>% 
  translate()
```

## Other details

Note that `model = TRUE` is needed to produce quantile predictions when there is a stratification variable and can be overridden in other cases.

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

The model formula can include _special_ terms, such as [survival::strata()]. The allows the model scale parameter to differ between groups contained in the function. The column used inside `strata()` is treated as qualitative no matter its type. 

For example, in this model, the numeric column `rx` is used to estimate two different scale parameters for each value of the column:

```{r}
library(survival)

surv_reg() %>% 
  fit(Surv(futime, fustat) ~ age + strata(rx), data = ovarian) %>% 
  extract_fit_engine()
```

## References

-  Kalbfleisch, J. D. and Prentice, R. L. 2002 _The statistical analysis of failure time data_, Wiley.
