```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("survival_reg", "flexsurvspline")`

## Tuning Parameters

This model has one engine-specific tuning parameter:

 * `k`: Number of knots in the spline. The default is `k = 0`.

## Translation from parsnip to the original package

`r uses_extension("survival_reg", "flexsurvspline", "censored regression")`

```{r}
#| label: flexsurvspline-creg
library(censored)

survival_reg() |> 
  set_engine("flexsurvspline") |> 
  set_mode("censored regression") |> 
  translate()
```

## Other details

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

For this engine, stratification cannot be specified via [`survival::strata()`], please see [flexsurv::flexsurvspline()] for alternative specifications.

```{r}
#| child: template-survival-mean.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```


## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```


## References

- Jackson, C. 2016. `flexsurv`: A Platform for Parametric Survival  Modeling in R. _Journal of Statistical Software_, 70(8), 1 - 33.
