```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("survival_reg", "flexsurv")`

## Tuning Parameters

```{r flexsurv-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("dist"),
                 default = c("'weibull'"))

param <-
  survival_reg() %>%
  set_engine("flexsurv") %>%
  set_mode("censored regression") %>%
    make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r flexsurv-param-list, echo = FALSE, results = "asis"}
param$item
```

## Translation from parsnip to the original package

`r uses_extension("survival_reg", "flexsurv", "censored regression")`

```{r flexsurv-creg}
library(censored)

survival_reg(dist = character(1)) %>% 
  set_engine("flexsurv") %>% 
  set_mode("censored regression") %>% 
  translate()
```

## Other details

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

For this engine, stratification cannot be specified via [`strata()`], please see the documentation of the [`flexsurv`] package for alternative specifications.

## References

- Jackson, C. 2016. `flexsurv`: A Platform for Parametric Survival  Modeling in R. _Journal of Statistical Software_, 70(8), 1 - 33.
