```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("surv_reg", "flexsurvspline")`

## Tuning Parameters

```{r flexsurvspline-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("num_knots"), default = 1L)

param <-
  surv_reg() %>%
  set_engine("flexsurvspline") %>%
  set_mode("censored regression") %>%
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r flexsurvspline-param-list, echo = FALSE, results = "asis"}
param$item
```

## Translation from parsnip to the original package

`r uses_extension("surv_reg", "flexsurvspline", "censored regression")`

```{r flexsurvspline-creg}
library(censored)

surv_reg() %>% 
  set_engine("flexsurvspline", num_knots = 1L) %>% 
  set_mode("censored regression") %>% 
  translate()
```

## Other details

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

For this engine, stratification cannot be specified via [`strata()`], please see [flexsurv::flexsurvspline()] for alternative specifications.

```{r child = "template-survival-mean.Rmd"}
```

## Saving fitted model objects

```{r child = "template-butcher.Rmd"}
```


## References

- Jackson, C. 2016. `flexsurv`: A Platform for Parametric Survival  Modeling in R. _Journal of Statistical Software_, 70(8), 1 - 33.
