```{r, child = "aaa.Rmd", include = FALSE}
```

`r descr_models("surv_reg", "survival")`

## Tuning Parameters

```{r flexsurv-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("dist"),
                 default = c("'weibull'"))

param <-
  surv_reg() %>%
  set_engine("flexsurv") %>%
  set_mode("regression") %>%
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r flexsurv-param-list, echo = FALSE, results = "asis"}
param$item
```


## Translation from parsnip to the original package

```{r flexsurv-reg, warning = FALSE}
surv_reg(dist = character(1)) %>% 
  set_engine("flexsurv") %>% 
  set_mode("regression") %>% 
  translate()
```

## Other details

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

For this engine, stratification cannot be specified via [`strata()`], please see the documentation of the flexsurv package for alternative specifications.

## References

- Jackson, C. 2016. `flexsurv`: A Platform for Parametric Survival  Modeling in R. _Journal of Statistical Software_, 70(8), 1 - 33.
