```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("survival_reg", "survival")`

## Tuning Parameters

```{r}
#| label: survival-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("dist"),
                 default = c("'weibull'"))

param <-
  survival_reg() |>
  set_engine("survival") |>
  set_mode("censored regression") |>
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: survival-param-list
#| echo: false
#| results: asis
param$item
```

## Translation from parsnip to the original package

`r uses_extension("survival_reg", "survival", "censored regression")`

```{r}
#| label: survival-creg
library(censored)

survival_reg(dist = character(1)) |> 
  set_engine("survival") |> 
  set_mode("censored regression") |> 
  translate()
```

## Other details

In the translated syntax above, note that `model = TRUE` is needed to produce quantile predictions when there is a stratification variable and can be overridden in other cases.

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

The model formula can include _special_ terms, such as [survival::strata()]. The allows the model scale parameter to differ between groups contained in the function. The column used inside `strata()` is treated as qualitative no matter its type. To learn more about using special terms in formulas with tidymodels, see [`?model_formula`][parsnip::model_formula].

For example, in this model, the numeric column `rx` is used to estimate two different scale parameters for each value of the column:

```{r}
library(survival)

survival_reg() |> 
  fit(Surv(futime, fustat) ~ age + strata(rx), data = ovarian) |> 
  extract_fit_engine()
```

```{r}
#| child: template-survival-mean.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```

## References

-  Kalbfleisch, J. D. and Prentice, R. L. 2002 _The statistical analysis of failure time data_, Wiley.
