```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("survival_reg", "flexsurv")`

## Tuning Parameters

```{r}
#| label: flexsurv-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("dist"),
                 default = c("'weibull'"))

param <-
  survival_reg() |>
  set_engine("flexsurv") |>
  set_mode("censored regression") |>
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: flexsurv-param-list
#| echo: false
#| results: asis
param$item
```

## Translation from parsnip to the original package

`r uses_extension("survival_reg", "flexsurv", "censored regression")`

```{r}
#| label: flexsurv-creg
library(censored)

survival_reg(dist = character(1)) |> 
  set_engine("flexsurv") |> 
  set_mode("censored regression") |> 
  translate()
```

## Other details

The main interface for this model uses the formula method since the model specification typically involved the use of [survival::Surv()]. 

For this engine, stratification cannot be specified via [`survival::strata()`], please see [flexsurv::flexsurvreg()] for alternative specifications.

```{r}
#| child: template-survival-mean.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```


## References

- Jackson, C. 2016. `flexsurv`: A Platform for Parametric Survival  Modeling in R. _Journal of Statistical Software_, 70(8), 1 - 33.
