# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below:

## LiblineaR

```{r LiblineaR-reg}
svm_linear() %>% 
  set_engine("LiblineaR") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r LiblineaR-cls}
svm_linear() %>% 
  set_engine("LiblineaR") %>% 
  set_mode("classification") %>% 
  translate()
```

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
## these values were manually checked :/ on 2021-02-01
get_defaults_svm_linear <- function() {
  tibble::tribble(
    ~model,    ~engine,       ~parsnip,        ~original,  ~default,
    "svm_linear", "LiblineaR",   "cost",          "C",        "1",
    "svm_linear", "LiblineaR",   "margin",        "svr_eps",  "0.1",
  )
}
convert_args("svm_linear")
```
