# Engine Details

```{r, child = "setup.Rmd", include = FALSE}
```

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below:

## kernlab

```{r kernlab-reg}
svm_rbf() %>% 
  set_engine("kernlab") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r kernlab-cls}
svm_rbf() %>% 
  set_engine("kernlab") %>% 
  set_mode("classification") %>% 
  translate()
```

## liquidSVM

```{r liquidSVM-reg}
svm_rbf() %>% 
  set_engine("liquidSVM") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r liquidSVM-cls}
svm_rbf() %>% 
  set_engine("liquidSVM") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that models created using the `liquidSVM` engine cannot be saved like
conventional R objects. The `fit` slot of the `model_fit` object has to be saved
separately using the `liquidSVM::write.liquidSVM()` function. Likewise to restore
a model, the `fit` slot has to be replaced with the model that is read using the
`liquidSVM::read.liquidSVM()` function.

`liquidSVM` parameterizes the kernel parameter differently than `kernlab`. To 
translate between engines, `sigma = 1/gammas^2`. Users will be specifying 
`sigma` and the function translates the value to `gamma`. 

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
## these values were manually checked :/ on 2020-05-28
get_defaults_svm_rbf <- function() {
  tibble::tribble(
    ~model,    ~engine,      ~parsnip,        ~original,  ~default,
    "svm_rbf", "kernlab",    "cost",          "C",        "1",
    "svm_rbf", "kernlab",    "rbf_sigma",     "sigma",    "varies",
    "svm_rbf", "kernlab",    "margin",        "epsilon",  "0.1",
    "svm_rbf", "liquidSVM",  "cost",          "lambdas",  "varies",
    "svm_rbf", "liquidSVM",  "rbf_sigma",     "gammas",   "varies",
  )
}
convert_args("svm_rbf")
```

