# Engine Details

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below:

## kernlab

```{r kernlab-reg}
svm_poly() %>% 
  set_engine("kernlab") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r kernlab-cls}
svm_poly() %>% 
  set_engine("kernlab") %>% 
  set_mode("classification") %>% 
  translate()
```

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters. Each engine typically has a 
different default value (shown in parentheses) for each parameter.

```{r echo = FALSE, results = "asis"}
## these values were manually checked :/ on 2020-05-28
get_defaults_svm_poly <- function() {
  tibble::tribble(
    ~model,     ~engine,    ~parsnip,        ~original,  ~default,
    "svm_poly", "kernlab",  "cost",          "C",        "1",
    "svm_poly", "kernlab",  "degree",        "degree",   "1",
    "svm_poly", "kernlab",  "scale_factor",  "scale",    "1",
    "svm_poly", "kernlab",  "margin",        "epsilon",  "0.1",
  )
}
parsnip::convert_args("svm_poly")
```

