# Engine Details

Engines may have pre-set default arguments when executing the model fit call. 
For this type of model, the template of the fit calls are below:

## kernlab

```{r kernlab-reg}
svm_rbf() %>% 
  set_engine("kernlab") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r kernlab-cls}
svm_rbf() %>% 
  set_engine("kernlab") %>% 
  set_mode("classification") %>% 
  translate()
```

## liquidSVM

```{r liquidSVM-reg}
svm_rbf() %>% 
  set_engine("liquidSVM") %>% 
  set_mode("regression") %>% 
  translate()
```

```{r liquidSVM-cls}
svm_rbf() %>% 
  set_engine("liquidSVM") %>% 
  set_mode("classification") %>% 
  translate()
```

Note that models created using the `liquidSVM` engine cannot be saved like
conventional R objects. The `fit` slot of the `model_fit` object has to be saved
separately using the `liquidSVM::write.liquidSVM()` function. Likewise to restore
a model, the `fit` slot has to be replaced with the model that is read using the
`liquidSVM::read.liquidSVM()` function.

`liquidSVM` parameterizes the kernel parameter differently than `kernlab`. To 
translate between engines, `sigma = 1/gammas^2`. Users will be specifying 
`sigma` and the function translates the value to `gamma`. 

## Parameter translations

The standardized parameter names in parsnip can be mapped to their original 
names in each engine that has main parameters:

```{r echo = FALSE, results = "asis"}
parsnip::convert_args("svm_rbf")
```

