```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("svm_linear", "LiblineaR")`

## Tuning Parameters

```{r LiblineaR-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("cost", "margin"),
                 default = c("1.0", "no default"))

param <-
  svm_linear() %>% 
  set_engine("LiblineaR") %>% 
  tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameters:

```{r LiblineaR-param-list, echo = FALSE, results = "asis"}
param$item
```

This engine fits models that are L2-regularized for L2-loss. In the [LiblineaR::LiblineaR()] documentation, these are types 1 (classification) and 11 (regression).

## Translation from parsnip to the original package (regression)

```{r LiblineaR-reg}
svm_linear(
  cost = double(1),
  margin = double(1)
) %>%  
  set_engine("LiblineaR") %>% 
  set_mode("regression") %>% 
  translate()
```

## Translation from parsnip to the original package (classification)

```{r LiblineaR-cls}
svm_linear(
  cost = double(1)
) %>% 
  set_engine("LiblineaR") %>% 
  set_mode("classification") %>% 
  translate()
```

The `margin` parameter does not apply to classification models. 

Note that the `LiblineaR` engine cannot produce class probabilities. When optimizing the model using the tune package, the default metrics require class probabilities. To be able to use the  `tune_*()` functions, a metric set must be passed as an argument and it can only contain metrics associated with hard class predictions (e.g., accuracy and so on).

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

## Working examples

```{r child = "template-reg-chicago.Rmd"}
```

We can define the model with specific parameters:

```{r}
svm_reg_spec <- 
  svm_linear(cost = 1, margin = 0.1) %>% 
  # This model can be used for classification or regression, so set mode
  set_mode("regression") %>% 
  set_engine("LiblineaR")
svm_reg_spec
```

Now we create the model fit object:

```{r}
set.seed(1)
svm_reg_fit <- svm_reg_spec %>% fit(ridership ~ ., data = Chicago_train)
svm_reg_fit
```

The holdout data can be predicted:

```{r}
predict(svm_reg_fit, Chicago_test)
```


```{r child = "template-cls-two-class.Rmd"}
```

We can define the model with specific parameters:

```{r}
svm_cls_spec <- 
  svm_linear(cost = 1) %>% 
  # This model can be used for classification or regression, so set mode
  set_mode("classification") %>% 
  set_engine("LiblineaR")
svm_cls_spec
```

Now we create the model fit object:

```{r}
set.seed(1)
svm_cls_fit <- svm_cls_spec %>% fit(Class ~ ., data = data_train)
svm_cls_fit
```

The holdout data can be predicted for hard class predictions.

```{r}
predict(svm_cls_fit, data_test)
```

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

