```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("svm_linear", "kernlab")`

## Tuning Parameters

```{r}
#| label: kernlab-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("cost", "margin"),
                 default = c("1.0", "0.1"))

param <-
  svm_linear() |> 
  set_engine("kernlab") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: kernlab-param-list
#| echo: false
#| results: asis
param$item
```

Parsnip changes the default range for `cost` to `c(-10, 5)`.

## Translation from parsnip to the original package (regression)

```{r}
#| label: kernlab-reg
svm_linear(
  cost = double(1),
  margin = double(1)
) |>  
  set_engine("kernlab") |> 
  set_mode("regression") |> 
  translate()
```

## Translation from parsnip to the original package (classification)

```{r}
#| label: kernlab-cls
svm_linear(
  cost = double(1)
) |> 
  set_engine("kernlab") |> 
  set_mode("classification") |> 
  translate()
```

The `margin` parameter does not apply to classification models. 

Note that the `"kernlab"` engine does not naturally estimate class probabilities. To produce them, the decision values of the model are converted to probabilities using Platt scaling. This method fits an additional model on top of the SVM model. When fitting the Platt scaling model, random numbers are used that are not reproducible or controlled by R's random number stream.   

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Saving fitted model objects

```{r}
#| child: template-butcher.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#svm-linear-kernlab) for `svm_linear()` with the `"kernlab"` engine.

## References

 - Lin, HT, and R Weng. ["A Note on Platt’s Probabilistic Outputs for Support Vector Machines"](https://www.csie.ntu.edu.tw/~cjlin/papers/plattprob.pdf)
 
 - Karatzoglou, A,  Smola, A,  Hornik, K, and A Zeileis. 2004. ["kernlab - An S4 Package for Kernel Methods in R."](https://www.jstatsoft.org/article/view/v011i09), _Journal of Statistical Software_. 
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

