```{r, child = "setup.Rmd", include = FALSE}
```

`r descr_models("svm_linear", "kernlab")`

## Tuning Parameters

```{r kernlab-param-info, echo = FALSE}
defaults <- 
  tibble::tibble(parsnip = c("cost", "margin"),
                 default = c("1.0", "0.1"))

param <-
  svm_linear() %>% 
  set_engine("kernlab") %>% 
  tunable() %>% 
  dplyr::select(-source, -component, -component_id, parsnip = name) %>% 
  dplyr::mutate(
    dials = purrr::map(call_info, get_dials),
    label = purrr::map_chr(dials, ~ .x$label),
    type = purrr::map_chr(dials, ~ .x$type)
  ) %>% 
  dplyr::full_join(defaults, by = "parsnip") %>% 
  mutate(
    item = 
      glue::glue("- `{parsnip}`: {label} (type: {type}, default: {default})\n\n")
  )
```

This model has `r nrow(param)` tuning parameters:

```{r kernlab-param-list, echo = FALSE, results = "asis"}
param$item
```

## Translation from parsnip to the original package (regression)

```{r kernlab-reg}
svm_linear(
  cost = double(1),
  margin = double(1)
) %>%  
  set_engine("kernlab") %>% 
  set_mode("regression") %>% 
  translate()
```

## Translation from parsnip to the original package (classification)

```{r kernlab-cls}
svm_linear(
  cost = double(1)
) %>% 
  set_engine("kernlab") %>% 
  set_mode("classification") %>% 
  translate()
```

The `margin` parameter does not apply to classification models. 

Note that the `kernlab` engine does not naturally estimate class probabilities. To get them, the decision values of the model are converted to probabilities using Platt scaling. This method fits an additional model on top of the SVM model. When fitting the Platt scaling model, random numbers are used that are not reproducible or controlled by R's random number stream.   

## Preprocessing requirements

```{r child = "template-makes-dummies.Rmd"}
```

```{r child = "template-same-scale.Rmd"}
```

## Working examples

```{r child = "template-reg-chicago.Rmd"}
```

We can define the model with specific parameters:

```{r}
svm_reg_spec <- 
  svm_linear(cost = 1, margin = 0.1) %>% 
  # This model can be used for classification or regression, so set mode
  set_mode("regression") %>% 
  set_engine("kernlab")
svm_reg_spec
```

Now we create the model fit object:

```{r}
set.seed(1)
svm_reg_fit <- svm_reg_spec %>% fit(ridership ~ ., data = Chicago_train)
svm_reg_fit
```

The holdout data can be predicted:

```{r}
predict(svm_reg_fit, Chicago_test)
```


```{r child = "template-cls-two-class.Rmd"}
```

```{r}
svm_cls_spec <- 
  svm_linear(cost = 1) %>% 
  # This model can be used for classification or regression, so set mode
  set_mode("classification") %>% 
  set_engine("kernlab")
svm_cls_spec
```

Now we create the model fit object:

```{r}
set.seed(1)
svm_cls_fit <- svm_cls_spec %>% fit(Class ~ ., data = data_train)
svm_cls_fit
```

The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

```{r}
predict(svm_cls_fit, data_test, type = "prob") %>% 
  bind_cols(
    predict(svm_cls_fit, data_test)
  )
```

## References

 - Lin, HT, and R Weng. ["A Note on Platt’s Probabilistic Outputs for Support Vector Machines"](https://www.csie.ntu.edu.tw/~cjlin/papers/plattprob.pdf)
 
 - Karatzoglou, A,  Smola, A,  Hornik, K, and A Zeileis. 2004. ["kernlab - An S4 Package for Kernel Methods in R."](https://www.jstatsoft.org/article/view/v011i09), _Journal of Statistical Software_. 
 
 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

