```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("svm_linear", "LiblineaR")`

## Tuning Parameters

```{r}
#| label: LiblineaR-param-info
#| echo: false
defaults <- 
  tibble::tibble(parsnip = c("cost", "margin"),
                 default = c("1.0", "no default"))

param <-
  svm_linear() |> 
  set_engine("LiblineaR") |> 
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: LiblineaR-param-list
#| echo: false
#| results: asis
param$item
```

This engine fits models that are L2-regularized for L2-loss. In the [LiblineaR::LiblineaR()] documentation, these are types 1 (classification) and 11 (regression).

Parsnip changes the default range for `cost` to `c(-10, 5)`.

## Translation from parsnip to the original package (regression)

```{r}
#| label: LiblineaR-reg
svm_linear(
  cost = double(1),
  margin = double(1)
) |>  
  set_engine("LiblineaR") |> 
  set_mode("regression") |> 
  translate()
```

## Translation from parsnip to the original package (classification)

```{r}
#| label: LiblineaR-cls
svm_linear(
  cost = double(1)
) |> 
  set_engine("LiblineaR") |> 
  set_mode("classification") |> 
  translate()
```

The `margin` parameter does not apply to classification models. 

Note that the `LiblineaR` engine does not produce class probabilities. When optimizing the model using the tune package, the default metrics require class probabilities. To use the  `tune_*()` functions, a metric set must be passed as an argument that only contains metrics for hard class predictions (e.g., accuracy).

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Sparse Data

```{r}
#| child: template-uses-sparse-data.Rmd
```

## Examples 

The "Fitting and Predicting with parsnip" article contains [examples](https://parsnip.tidymodels.org/articles/articles/Examples.html#svm-linear-LiblineaR) for `svm_linear()` with the `"LiblineaR"` engine.

## References

 - Kuhn, M, and K Johnson. 2013. _Applied Predictive Modeling_. Springer.

