```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("tabular_saint", "brulee")`

## Tuning Parameters

```{r}
#| label: brulee-param-info
#| echo: false
defaults <-
  tibble::tibble(
    parsnip =
      c("epochs", "num_embedding", "attention_type", "num_attn_heads",
        "num_attn_blocks", "dropout_attn", "dropout_hidden", "dropout_last",
        "hidden_units", "hidden_activations", "target_token", "penalty",
        "mixture", "learn_rate", "rate_schedule", "momentum", "batch_size",
        "class_weights", "stop_iter"),
    default = c("100L", "32L", "'both'", "8L",
                "6L", "0.1", "0.1", "0.0",
                "5L", "'relu'", "TRUE", "0.001",
                "0.0", "0.0001", "'none'", "0.0", "NULL",
                "NULL", "5L"))

spec <-
  tabular_saint(
    epochs = tune(),
    num_embedding = tune(),
    attention_type = tune(),
    num_attn_heads = tune(),
    num_attn_blocks = tune(),
    dropout_attn = tune(),
    dropout_hidden = tune(),
    dropout_last = tune(),
    hidden_units = tune(),
    hidden_activations = tune(),
    target_token = tune(),
    penalty = tune(),
    mixture = tune(),
    learn_rate = tune(),
    rate_schedule = tune(),
    momentum = tune(),
    batch_size = tune(),
    class_weights = tune(),
    stop_iter = tune()
  ) |>
  set_engine("brulee")

param <- spec |> make_parameter_list(defaults)

```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: brulee-param-list
#| echo: false
#| results: asis
param$item
```

The use of the L1 penalty (a.k.a. the lasso penalty) does _not_ force parameters to be strictly zero (as it does in packages such as glmnet). The zeroing out of parameters is a specific feature the optimization method used in those packages.

When `attention_type` is `"row"` or `"both"`, SAINT applies inter-sample (row) attention across the samples in a batch. The engine keeps this on at prediction time by default, so the prediction for a given row depends on which other rows are passed to `predict()` in the same call. To obtain batch-independent predictions, bypass row attention at predict time with `set_engine("brulee", row_attention_on_predict = FALSE)`.

## Translation from parsnip to the original package (regression)

```{r}
#| label: brulee-reg
tabular_saint(
  epochs = integer(1),
  num_embedding = integer(1),
  attention_type = character(1),
  num_attn_heads = integer(1),
  num_attn_blocks = integer(1),
  dropout_attn = double(1),
  dropout_hidden = double(1),
  dropout_last = double(1),
  hidden_units = integer(1),
  hidden_activations = character(1),
  target_token = logical(1),
  penalty = double(1),
  mixture = double(1),
  learn_rate = double(1),
  rate_schedule = character(1),
  momentum = double(1),
  batch_size = NULL,
  class_weights = NULL,
  stop_iter = integer(1)
) |>
  set_engine("brulee") |>
  set_mode("regression") |>
  translate()
```

Note that parsnip automatically sets linear activation in the last layer.

## Translation from parsnip to the original package (classification)

```{r}
#| label: brulee-cls
tabular_saint(
  epochs = integer(1),
  num_embedding = integer(1),
  attention_type = character(1),
  num_attn_heads = integer(1),
  num_attn_blocks = integer(1),
  dropout_attn = double(1),
  dropout_hidden = double(1),
  dropout_last = double(1),
  hidden_units = integer(1),
  hidden_activations = character(1),
  target_token = logical(1),
  penalty = double(1),
  mixture = double(1),
  learn_rate = double(1),
  rate_schedule = character(1),
  momentum = double(1),
  batch_size = NULL,
  class_weights = NULL,
  stop_iter = integer(1)
) |>
  set_engine("brulee") |>
  set_mode("classification") |>
  translate()
```

## Preprocessing requirements

`brulee_saint()` natively handles factor predictors via learned embeddings. Factor columns are automatically detected and embedded, while numeric columns use a scaled embedding. There is _no need to pre-encode factors as indicators_.

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("tabular_saint_predict") |>
  dplyr::filter(engine == "brulee") |>
  dplyr::select(mode, type)

```

## References

 - Somepalli, G., Goldblum, M., Schwarzschild, A., Bruss, C. B., & Goldstein, T. (2021). SAINT: Improved Neural Networks for Tabular Data via Row Attention and Contrastive Pre-Training. _arXiv preprint_ arXiv:2106.01342.
