```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("tabular_resnet", "brulee")`

## Tuning Parameters

```{r}
#| label: brulee-param-info
#| echo: false
defaults <-
  tibble::tibble(
    parsnip =
      c("epochs", "hidden_units", "bottleneck_units", "residual_at",
        "activation", "penalty", "mixture", "dropout", "learn_rate",
        "rate_schedule", "momentum", "batch_size", "class_weights",
        "stop_iter"),
    default = c("100L", "3L", "same as hidden_units", "NULL",
                "'relu'", "0.001", "0.0", "0.0", "0.01",
                "'none'", "0.0", "NULL", "NULL",
                "5L"))

spec <-
  tabular_resnet(
    epochs = tune(),
    hidden_units = tune(),
    bottleneck_units = tune(),
    residual_at = tune(),
    activation = tune(),
    penalty = tune(),
    mixture = tune(),
    dropout = tune(),
    learn_rate = tune(),
    rate_schedule = tune(),
    momentum = tune(),
    batch_size = tune(),
    class_weights = tune(),
    stop_iter = tune()
  ) |>
  set_engine("brulee")

param <- spec |> make_parameter_list(defaults)

```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: brulee-param-list
#| echo: false
#| results: asis
param$item
```

The use of the L1 penalty (a.k.a. the lasso penalty) does _not_ force parameters to be strictly zero (as it does in packages such as glmnet). The zeroing out of parameters is a specific feature the optimization method used in those packages.

## Translation from parsnip to the original package (regression)

```{r}
#| label: brulee-reg
tabular_resnet(
  epochs = integer(1),
  hidden_units = integer(1),
  bottleneck_units = integer(1),
  residual_at = NULL,
  activation = character(1),
  penalty = double(1),
  mixture = double(1),
  dropout = double(1),
  learn_rate = double(1),
  rate_schedule = character(1),
  momentum = double(1),
  batch_size = NULL,
  class_weights = NULL,
  stop_iter = integer(1)
) |>
  set_engine("brulee") |>
  set_mode("regression") |>
  translate()
```

Note that parsnip automatically sets linear activation in the last layer.

## Translation from parsnip to the original package (classification)

```{r}
#| label: brulee-cls
tabular_resnet(
  epochs = integer(1),
  hidden_units = integer(1),
  bottleneck_units = integer(1),
  residual_at = NULL,
  activation = character(1),
  penalty = double(1),
  mixture = double(1),
  dropout = double(1),
  learn_rate = double(1),
  rate_schedule = character(1),
  momentum = double(1),
  batch_size = NULL,
  class_weights = NULL,
  stop_iter = integer(1)
) |>
  set_engine("brulee") |>
  set_mode("classification") |>
  translate()
```

## Preprocessing requirements

`brulee_resnet()` requires numeric predictors. Factor or categorical predictors need to be converted to numeric values (e.g., dummy or indicator variables) before fitting; parsnip does _not_ create indicator variables for this engine, so use a recipe (or some other method) to make them numeric.

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("tabular_resnet_predict") |>
  dplyr::filter(engine == "brulee") |>
  dplyr::select(mode, type)

```

## References

 - Gorishniy, Y., Rubachev, I., Khrulkov, V., & Babenko, A. (2021). Revisiting deep learning models for tabular data. _Advances in Neural Information Processing Systems_, 34.
