```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("tabular_pfn", "tabpfn")`

## Tuning Parameters

```{r}
#| label: tabpfn-param-info
#| echo: false
defaults <-
  tibble::tibble(
    parsnip = c("num_estimators", "softmax_temperature",
                "balance_probabilities", "average_before_softmax"),
    default = c("8L", "0.9", "FALSE", "FALSE"))

spec <-
  tabular_pfn(
    num_estimators = tune(),
    softmax_temperature = tune(),
    balance_probabilities = tune(),
    average_before_softmax = tune()
  ) |>
  set_engine("tabpfn")

param <- spec |> make_parameter_list(defaults)

```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: tabpfn-param-list
#| echo: false
#| results: asis
param$item
```

TabPFN is a pretrained (prior-data fitted) network; no weights are updated when the model is fit. The training set is ingested at fit time and predictions are made via in-context learning.

Other engine arguments of interest:

 - `training_set_limit`: the maximum number of training set rows used for in-context learning.
 - `control`: a list of options produced by `tabpfn::control_tab_pfn()`.

The tabpfn package runs the Python "tabpfn" library via reticulate, so a working Python environment is required; the package can create one automatically on first use. The pretrained model weights are downloaded from Hugging Face the first time a model is fit, and the model's license contains provisions for non-commercial use. See [tabpfn::tab_pfn()] for details on all of these topics.

## Translation from parsnip to the original package (regression)

```{r}
#| label: tabpfn-reg
tabular_pfn(
  num_estimators = integer(1),
  softmax_temperature = double(1),
  balance_probabilities = logical(1),
  average_before_softmax = logical(1)
) |>
  set_engine("tabpfn") |>
  set_mode("regression") |>
  translate()
```

## Translation from parsnip to the original package (classification)

```{r}
#| label: tabpfn-cls
tabular_pfn(
  num_estimators = integer(1),
  softmax_temperature = double(1),
  balance_probabilities = logical(1),
  average_before_softmax = logical(1)
) |>
  set_engine("tabpfn") |>
  set_mode("classification") |>
  translate()
```

## Preprocessing requirements

Predictors do not require preprocessing; missing values and factor predictors are allowed and are handled internally by the model. There is _no need to pre-encode factors as indicators_ or to scale the predictors.

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("tabular_pfn_predict") |>
  dplyr::filter(engine == "tabpfn") |>
  dplyr::select(mode, type)

```

## References

 - Hollmann, N., Müller, S., Purucker, L., Krishnakumar, A., Körfer, M., Hoo, S. B., Schirrmeister, R. T., & Hutter, F. (2025). Accurate predictions on small data with a tabular foundation model. _Nature_, 637(8045), 319-326.

 - Hollmann, N., Müller, S., Eggensperger, K., & Hutter, F. (2022). TabPFN: A transformer that solves small tabular classification problems in a second. _arXiv preprint_ arXiv:2207.01848.

 - Müller, S., Hollmann, N., Pineda Arango, S., Grabocka, J., & Hutter, F. (2021). Transformers can do Bayesian inference. _arXiv preprint_ arXiv:2112.10510.
