```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("tabular_auto_int", "brulee")`

## Tuning Parameters

```{r}
#| label: brulee-param-info
#| echo: false
defaults <- 
  tibble::tibble(
    parsnip = 
      c("epochs", "num_embedding", "hidden_units", "hidden_activations", 
        "num_attn_feat", "num_attn_heads", "num_attn_blocks", "activation", 
        "dropout", "dropout_attn", "dropout_embedding", "penalty", "mixture", 
        "learn_rate", "rate_schedule", "momentum", "batch_size", "class_weights", 
        "stop_iter"),
    default = c("100L", "16L", "NULL", "NULL", 
                "16L", "2L", "3L", "'relu'",
                "0.0", "0.0", "0.0", "0.001", "0.0",
                "0.01", "'none'", "0.0", "NULL", "NULL",
                "5L"))

spec <-
  tabular_auto_int(
    epochs = tune(),
    num_embedding = tune(),
    hidden_units = tune(),
    hidden_activations = tune(),
    num_attn_feat = tune(),
    num_attn_heads = tune(),
    num_attn_blocks = tune(),
    activation = tune(),
    dropout = tune(),
    dropout_attn = tune(),
    dropout_embedding = tune(),
    penalty = tune(),
    mixture = tune(),
    learn_rate = tune(),
    rate_schedule = tune(),
    momentum = tune(),
    batch_size = tune(),
    class_weights = tune(),
    stop_iter = tune()
  ) |> 
  set_engine("brulee")

param <- spec |> make_parameter_list(defaults)

```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: brulee-param-list
#| echo: false
#| results: asis
param$item
```

The use of the L1 penalty (a.k.a. the lasso penalty) does _not_ force parameters to be strictly zero (as it does in packages such as glmnet). The zeroing out of parameters is a specific feature the optimization method used in those packages.

## Translation from parsnip to the original package (regression)

```{r}
#| label: brulee-reg
library(tabby)

tabular_auto_int(
  epochs = integer(1),
  num_embedding = integer(1),
  hidden_units = NULL,
  hidden_activations = NULL,
  num_attn_feat = integer(1),
  num_attn_heads = integer(1),
  num_attn_blocks = integer(1),
  activation = character(1),
  dropout = double(1),
  dropout_attn = double(1),
  dropout_embedding = double(1),
  penalty = double(1),
  mixture = double(1),
  learn_rate = double(1),
  rate_schedule = tune(),
  momentum = character(1),
  batch_size = NULL,
  class_weights = NULL,
  stop_iter = integer(1)
  ) |>  
  set_engine("brulee") |> 
  set_mode("regression") |> 
  translate()
```

Note that parsnip automatically sets linear activation in the last layer. 

## Translation from parsnip to the original package (classification)

```{r}
#| label: brulee-cls
library(tabby)

tabular_auto_int(
  epochs = integer(1),
  num_embedding = integer(1),
  hidden_units = NULL,
  hidden_activations = NULL,
  num_attn_feat = integer(1),
  num_attn_heads = integer(1),
  num_attn_blocks = integer(1),
  activation = character(1),
  dropout = double(1),
  dropout_attn = double(1),
  dropout_embedding = double(1),
  penalty = double(1),
  mixture = double(1),
  learn_rate = double(1),
  rate_schedule = tune(),
  momentum = character(1),
  batch_size = NULL,
  class_weights = NULL,
  stop_iter = integer(1)
) |> 
  set_engine("brulee") |> 
  set_mode("classification") |> 
  translate()
```

## Preprocessing requirements

`brulee_auto_int()` natively handles factor predictors via learned embeddings. Factor columns are automatically detected and embedded, while numeric columns use a scaled embedding. There is _no need to pre-encode factors as indicators_.

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("tabular_auto_int_predict") |>
  dplyr::filter(engine == "brulee") |>
  dplyr::select(mode, type)

```

## References

 - Song, W., Shi, C., Xiao, Z., Duan, Z., Xu, Y., Zhang, M., & Tang, J. (2019). AutoInt: Automatic Feature Interaction Learning via Self-Attentive Neural Networks. In _Proceedings of the 28th ACM International Conference on Information and Knowledge Management (CIKM)_.



