```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("tabular_rln", "brulee")`

## Tuning Parameters

```{r}
#| label: brulee-param-info
#| echo: false
defaults <-
  tibble::tibble(
    parsnip =
      c("hidden_units", "penalty_type", "penalty_average", "step_rate",
        "activation", "epochs", "learn_rate", "rate_schedule", "momentum",
        "batch_size", "stop_iter"),
    default = c("5L", "'L1'", "1e-10", "1e6",
                "'relu'", "100L", "0.001", "'none'", "0.0",
                "NULL", "20L"))

spec <-
  tabular_rln(
    hidden_units = tune(),
    penalty_type = tune(),
    penalty_average = tune(),
    step_rate = tune(),
    activation = tune(),
    epochs = tune(),
    learn_rate = tune(),
    rate_schedule = tune(),
    momentum = tune(),
    batch_size = tune(),
    stop_iter = tune()
  ) |>
  set_engine("brulee")

param <- spec |> make_parameter_list(defaults)

```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: brulee-param-list
#| echo: false
#| results: asis
param$item
```

`penalty_average` and `step_rate` are specified on the natural scale but are best tuned on the log10 scale.

## Translation from parsnip to the original package (regression)

```{r}
#| label: brulee-reg
library(tabby)

tabular_rln(
  hidden_units = integer(1),
  penalty_type = character(1),
  penalty_average = double(1),
  step_rate = double(1),
  activation = character(1),
  epochs = integer(1),
  learn_rate = double(1),
  rate_schedule = character(1),
  momentum = double(1),
  batch_size = NULL,
  stop_iter = integer(1)
) |>
  set_engine("brulee") |>
  set_mode("regression") |>
  translate()
```

## Preprocessing requirements

`brulee_rln()` requires numeric predictors. Factor or categorical predictors need to be converted to numeric values (e.g., dummy or indicator variables) before fitting; parsnip does _not_ create indicator variables for this engine, so use a recipe (or some other method) to make them numeric.

```{r}
#| child: template-same-scale.Rmd
```

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("tabular_rln_predict") |>
  dplyr::filter(engine == "brulee") |>
  dplyr::select(mode, type)

```

## References

 - Shavitt, I., & Segal, E. (2018). Regularization learning networks: Deep learning for tabular datasets. _Advances in Neural Information Processing Systems_, 31, 1379-1389.
