```{r}
#| child: aaa.Rmd
#| include: false
```

`r descr_models("tabular_icl", "brulee")`

## Tuning Parameters

```{r}
#| label: brulee-param-info
#| echo: false
defaults <-
  tibble::tibble(
    parsnip = c("num_estimators", "softmax_temperature"),
    default = c("8L", "0.9"))

spec <-
  tabular_icl(
    num_estimators = tune(),
    softmax_temperature = tune()
  ) |>
  set_engine("brulee")

param <- spec |> make_parameter_list(defaults)

```

This model has `r nrow(param)` tuning parameters:

```{r}
#| label: brulee-param-list
#| echo: false
#| results: asis
param$item
```

TabICL is a pretrained (prior-data fitted) network; no weights are updated when the model is fit. The training set is ingested at fit time and predictions are made via in-context learning.

Other engine arguments of interest:

 - `normalization`: a character vector of per-member normalization methods (`"none"` or `"YeoJohnson"`).
 - `training_set_limit`: the maximum number of training set rows used for in-context learning.
 - `device`: the torch device to use (e.g., `"cpu"`).

## Translation from parsnip to the original package (regression)

```{r}
#| label: brulee-reg
tabular_icl(
  num_estimators = integer(1),
  softmax_temperature = double(1)
) |>
  set_engine("brulee") |>
  set_mode("regression") |>
  translate()
```

## Translation from parsnip to the original package (classification)

```{r}
#| label: brulee-cls
tabular_icl(
  num_estimators = integer(1),
  softmax_temperature = double(1)
) |>
  set_engine("brulee") |>
  set_mode("classification") |>
  translate()
```

## Preprocessing requirements

`brulee_tab_icl()` converts each predictor column to a numeric value internally: factor and character columns are ordinal-encoded and numeric columns are standardized (with an optional Yeo-Johnson transformation) inside the model. There is _no need to pre-encode factors as indicators_; a wide one-hot expansion degrades prediction quality for this model. Predictors also do not need to be scaled by the user.

## Case weights

```{r}
#| child: template-no-case-weights.Rmd
```

## Prediction types

```{r}
#| label: predict-types

parsnip:::get_from_env("tabular_icl_predict") |>
  dplyr::filter(engine == "brulee") |>
  dplyr::select(mode, type)

```

## References

 - Qu, J., Holzmüller, D., Varoquaux, G., & Morvan, M. L. (2025). TabICL: A tabular foundation model for in-context learning on large data. _arXiv preprint_ arXiv:2502.05564.

 - Qu, J., Holzmüller, D., Varoquaux, G., & Morvan, M. L. (2026). TabICLv2: A better, faster, scalable, and open tabular foundation model. _arXiv preprint_ arXiv:2602.11139.
