---
title: "Fitting and predicting with parsnip"
output: rmarkdown::html_vignette
description: |
  This vignette  show how to **fit** and **predict** with different 
  combinations of model, mode, and engine.
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Fitting and predicting with parsnip}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: startup
#| include: false
library(utils)
library(ggplot2)
theme_set(theme_bw())
```

These examples show how to *fit* and *predict* with different combinations of model, mode, and engine. As a reminder, in parsnip, 

- the **model type** differentiates basic modeling approaches, such as random forests, logistic regression, linear support vector machines, etc.,

- the **mode** denotes in what kind of modeling context it will be used (most commonly, classification or regression), and

- the computational **engine** indicates how the model is fit, such as with a specific R package implementation or even methods outside of R like Keras or Stan.

The following examples use consistent data sets throughout. For regression, we use the Chicago ridership data. For classification, we use an artificial data set for a binary example and the Palmer penguins data for a multiclass example.


## `bart()` models

  <details id="bart-dbarts"> 
  
  <summary>With the `"dbarts"` engine</summary>
  
  <h3>Regression Example (`dbarts`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  bt_reg_spec <- 
    bart(trees = 15) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("dbarts")
  bt_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  bt_reg_fit <- bt_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  bt_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(bt_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`dbarts`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  bt_cls_spec <- 
    bart(trees = 15) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("dbarts")
  bt_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  bt_cls_fit <- bt_cls_spec |> fit(Class ~ ., data = data_train)
  bt_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(bt_cls_fit, data_test),
    predict(bt_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


## `boost_tree()` models

  <details id="boost-tree-xgboost"> 
  
  <summary>With the `"xgboost"` engine</summary>
  
  <h3>Regression Example (`xgboost`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  bt_reg_spec <- 
    boost_tree(trees = 15) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("xgboost")
  bt_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  bt_reg_fit <- bt_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  bt_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(bt_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`xgboost`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  bt_cls_spec <- 
    boost_tree(trees = 15) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("xgboost")
  bt_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  bt_cls_fit <- bt_cls_spec |> fit(Class ~ ., data = data_train)
  bt_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(bt_cls_fit, data_test),
    predict(bt_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


  <details id="boost-tree-C5.0"> 
  
  <summary>With the `"C5.0"` engine</summary>

  <h3>Classification Example (`C5.0`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  bt_cls_spec <- 
    boost_tree(trees = 15) |> 
    set_mode("classification") |> 
    set_engine("C5.0")
  bt_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  bt_cls_fit <- bt_cls_spec |> fit(Class ~ ., data = data_train)
  bt_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(bt_cls_fit, data_test),
    predict(bt_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>  
  
  
## `decision_tree()` models

  <details id="decision-tree-rpart"> 
  
  <summary>With the `"rpart"` engine</summary>
  
  <h3>Regression Example (`rpart`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  dt_reg_spec <- 
    decision_tree(tree_depth = 30) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("rpart")
  dt_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  dt_reg_fit <- dt_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  dt_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(dt_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`rpart`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  dt_cls_spec <- 
    decision_tree(tree_depth = 30) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("rpart")
  dt_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  dt_cls_fit <- dt_cls_spec |> fit(Class ~ ., data = data_train)
  dt_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(dt_cls_fit, data_test),
    predict(dt_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
  
  
  <details id="decision-tree-C5.0"> 
  
  <summary>With the `"C5.0"` engine</summary>
  
  <h3>Classification Example (`C5.0`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  dt_cls_spec <- 
    decision_tree(min_n = 2) |> 
    set_mode("classification") |> 
    set_engine("C5.0")
  dt_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  dt_cls_fit <- dt_cls_spec |> fit(Class ~ ., data = data_train)
  dt_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(dt_cls_fit, data_test),
    predict(dt_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>

## `gen_additive_mod()` models

  <details id="gen-additive-mod-mgcv"> 
  
  <summary>With the `"mgcv"` engine</summary>
  
  <h3>Regression Example (`mgcv`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  gam_reg_spec <- 
    gen_additive_mod(select_features = FALSE, adjust_deg_free = 10) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("mgcv")
  gam_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  gam_reg_fit <- gam_reg_spec |> 
    fit(ridership ~ Clark_Lake + Quincy_Wells, data = Chicago_train)
  gam_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(gam_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`mgcv`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  gam_cls_spec <- 
    gen_additive_mod(select_features = FALSE, adjust_deg_free = 10) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("mgcv")
  gam_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  gam_cls_fit <- gam_cls_spec |> fit(Class ~ A + B, data = data_train)
  gam_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(gam_cls_fit, data_test),
    predict(gam_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>

  
## `linear_reg()` models

  <details id="linear-reg-lm"> 
  
  <summary>With the `"lm"` engine</summary>
  
  <h3>Regression Example (`lm`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  linreg_reg_spec <- 
    linear_reg() |> 
    set_engine("lm")
  linreg_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  linreg_reg_fit <- linreg_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  linreg_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(linreg_reg_fit, Chicago_test)
  ```
    
  </details>

  <details id="linear-reg-glm"> 
  
  <summary>With the `"glm"` engine</summary>
  
  <h3>Regression Example (`glm`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  linreg_reg_spec <- 
    linear_reg() |> 
    set_engine("glm")
  linreg_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  linreg_reg_fit <- linreg_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  linreg_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(linreg_reg_fit, Chicago_test)
  ```
    
  </details>

  <details id="linear-reg-glmnet"> 
  
  <summary>With the `"glmnet"` engine</summary>

  <h3>Regression Example (`glmnet`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  linreg_reg_spec <- 
    linear_reg(penalty = 0.1) |> 
    set_engine("glmnet")
  linreg_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  linreg_reg_fit <- linreg_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  linreg_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(linreg_reg_fit, Chicago_test)
  ```
    
  </details>


  <details id="linear-reg-keras"> 
  
  <summary>With the `"keras"` engine</summary>
  
  <h3>Regression Example (`keras`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  linreg_reg_spec <- 
    linear_reg(penalty = 0.1) |> 
    set_engine("keras")
  linreg_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  linreg_reg_fit <- linreg_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  linreg_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(linreg_reg_fit, Chicago_test)
  ```
    
  </details>


  <details id="linear-reg-stan"> 
  
  <summary>With the `"stan"` engine</summary>
  
  <h3>Regression Example (`stan`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  linreg_reg_spec <- 
    linear_reg() |> 
    set_engine("stan")
  linreg_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  linreg_reg_fit <- linreg_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  linreg_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(linreg_reg_fit, Chicago_test)
  ```
    
  </details>

  <details id="linear-reg-quantreg"> 
  
  <summary>With the `"quantreg"` engine</summary>
  
  <h3>Quantile regression Example (`quantreg`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-sacramento.R")
  ```

  We can define the model but should set the model mode. Also, for these models the levels of the distirunbtion that we would like to predict need to specified with the mode using the `quantile_levels` argument. Let's predict the 0.25, 0.50, and 0.75 quantiles:

  ```{r}
  linreg_quant_spec <- 
    linear_reg() |> 
    set_engine("quantreg") |> 
    set_mode("quantile regression", quantile_levels = (1:3) / 4)
  linreg_quant_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  linreg_quant_fit <- linreg_quant_spec |> fit(price ~ sqft, data = sac_train)
  linreg_quant_fit
  ```

  The holdout data can be predicted:

  ```{r}
  quant_pred <- predict(linreg_quant_fit, sac_test)
  quant_pred
  ```
  
  `.pred_quantile` is a vector type that contains all of the quartile predictions for each row.  You can convert this to a rectangular data set using either of: 
  
  ```{r}
  as.matrix(quant_pred$.pred_quantile)
  
  # or 
  as_tibble(quant_pred$.pred_quantile)
  ```
  
  </details>

  <details id="linear-reg-brulee"> 
  
  <summary>With the `"brulee"` engine</summary>
  
  <h3>Regression Example (`brulee`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  linreg_reg_spec <- 
    linear_reg() |> 
    set_engine("brulee")
  linreg_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  linreg_reg_fit <- linreg_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  linreg_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(linreg_reg_fit, Chicago_test)
  ```
    
  </details>
  
## `logistic_reg()` models

  <details id="logistic-reg-glm"> 
  
  <summary>With the `"glm"` engine</summary>
  
  <h3>Classification Example (`glm`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  logreg_cls_spec <- 
    logistic_reg() |> 
    set_engine("glm")
  logreg_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  logreg_cls_fit <- logreg_cls_spec |> fit(Class ~ ., data = data_train)
  logreg_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(logreg_cls_fit, data_test),
    predict(logreg_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
  
  
  <details id="logistic-reg-glmnet"> 
  
  <summary>With the `"glmnet"` engine</summary>

  <h3>Classification Example (`glmnet`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  logreg_cls_spec <- 
    logistic_reg(penalty = 0.1) |> 
    set_engine("glmnet")
  logreg_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  logreg_cls_fit <- logreg_cls_spec |> fit(Class ~ ., data = data_train)
  logreg_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(logreg_cls_fit, data_test),
    predict(logreg_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
  
  
  <details id="logistic-reg-keras"> 
  
  <summary>With the `"keras"` engine</summary>

  <h3>Classification Example (`keras`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  logreg_cls_spec <- 
    logistic_reg(penalty = 0.1) |> 
    set_engine("keras")
  logreg_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  logreg_cls_fit <- logreg_cls_spec |> fit(Class ~ ., data = data_train)
  logreg_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(logreg_cls_fit, data_test),
    predict(logreg_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


  <details id="logistic-reg-LiblineaR"> 
  
  <summary>With the `"LiblineaR"` engine</summary>

  <h3>Classification Example (`LiblineaR`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  logreg_cls_spec <- 
    logistic_reg(penalty = 0.1) |> 
    set_engine("LiblineaR")
  logreg_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  logreg_cls_fit <- logreg_cls_spec |> fit(Class ~ ., data = data_train)
  logreg_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(logreg_cls_fit, data_test),
    predict(logreg_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


  <details id="logistic-reg-stan"> 
  
  <summary>With the `"stan"` engine</summary>
  
  <h3>Classification Example (`stan`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  logreg_cls_spec <- 
    logistic_reg() |> 
    set_engine("stan")
  logreg_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  logreg_cls_fit <- logreg_cls_spec |> fit(Class ~ ., data = data_train)
  logreg_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(logreg_cls_fit, data_test),
    predict(logreg_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


  <details id="logistic-reg-brulee"> 
  
  <summary>With the `"brulee"` engine</summary>
  
  <h3>Classification Example (`brulee`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  logreg_cls_spec <- 
    logistic_reg() |> 
    set_engine("brulee")
  logreg_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  logreg_cls_fit <- logreg_cls_spec |> fit(Class ~ ., data = data_train)
  logreg_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(logreg_cls_fit, data_test),
    predict(logreg_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
  
## `mars()` models 

  <details id="mars-earth"> 
  
  <summary>With the `"earth"` engine</summary>

  <h3>Regression Example (`earth`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mars_reg_spec <- 
    mars(prod_degree = 1, prune_method = "backward") |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("earth")
  mars_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mars_reg_fit <- mars_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  mars_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(mars_reg_fit, Chicago_test)
  ```

  <h3>Classification Example (`earth`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mars_cls_spec <- 
    mars(prod_degree = 1, prune_method = "backward") |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("earth")
  mars_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mars_cls_fit <- mars_cls_spec |> fit(Class ~ ., data = data_train)
  mars_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mars_cls_fit, data_test),
    predict(mars_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


## `mlp()` models

  <details id="mlp-nnet"> 
  
  <summary>With the `"nnet"` engine</summary>

  <h3>Regression Example (`nnet`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_reg_spec <- 
    mlp(penalty = 0, epochs = 100) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("nnet")
  mlp_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mlp_reg_fit <- mlp_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  mlp_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(mlp_reg_fit, Chicago_test)
  ```

  <h3>Classification Example (`nnet`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_cls_spec <- 
    mlp(penalty = 0, epochs = 100) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("nnet")
  mlp_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mlp_cls_fit <- mlp_cls_spec |> fit(Class ~ ., data = data_train)
  mlp_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mlp_cls_fit, data_test),
    predict(mlp_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
  
  <details id="mlp-keras"> 
  
  <summary>With the `"keras"` engine</summary>

  <h3>Regression Example (`keras`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_reg_spec <- 
    mlp(penalty = 0, epochs = 20) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("keras")
  mlp_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mlp_reg_fit <- mlp_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  mlp_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(mlp_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`keras`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_cls_spec <- 
    mlp(penalty = 0, epochs = 20) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("keras")
  mlp_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mlp_cls_fit <- mlp_cls_spec |> fit(Class ~ ., data = data_train)
  mlp_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mlp_cls_fit, data_test),
    predict(mlp_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>  
  

  <details id="mlp-brulee"> 
  
  <summary>With the `"brulee"` engine</summary>

  <h3>Regression Example (`brulee`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_reg_spec <- 
    mlp(penalty = 0, epochs = 100) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("brulee")
  mlp_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mlp_reg_fit <- mlp_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  mlp_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(mlp_reg_fit, Chicago_test)
  ```

  <h3>Classification Example (`brulee`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_cls_spec <- 
    mlp(penalty = 0, epochs = 100) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("brulee")
  mlp_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mlp_cls_fit <- mlp_cls_spec |> fit(Class ~ ., data = data_train)
  mlp_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mlp_cls_fit, data_test),
    predict(mlp_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
  
  <details id="mlp-brulee_two_layer_two_layer"> 
  
  <summary>With the `"brulee_two_layer"` engine</summary>

  <h3>Regression Example (`brulee_two_layer`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_reg_spec <- 
    mlp(penalty = 0, epochs = 10) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("brulee_two_layer", hidden_units_2 = 2)
  mlp_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(13)
  mlp_reg_fit <- mlp_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  mlp_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(mlp_reg_fit, Chicago_test)
  ```

  <h3>Classification Example (`brulee_two_layer`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mlp_cls_spec <- 
    mlp(penalty = 0, epochs = 10) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("brulee_two_layer", hidden_units_2 = 2)
  mlp_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(12)
  mlp_cls_fit <- mlp_cls_spec |> fit(Class ~ ., data = data_train)
  mlp_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mlp_cls_fit, data_test),
    predict(mlp_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
  
  
## `multinom_reg()` models

  <details id="multinom-reg-glmnet"> 

  <summary>With the `"glmnet"` engine</summary>

  <h3>Classification Example (`glmnet`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-multi-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mr_cls_spec <- 
    multinom_reg(penalty = 0.1) |> 
    set_engine("glmnet")
  mr_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mr_cls_fit <- mr_cls_spec |> fit(island ~ ., data = penguins_train)
  mr_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mr_cls_fit, penguins_test),
    predict(mr_cls_fit, penguins_test, type = "prob")
  )
  ```

  </details>


  <details id="multinom-reg-keras"> 

  <summary>With the `"keras"` engine</summary>

  <h3>Classification Example (`keras`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-multi-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mr_cls_spec <- 
    multinom_reg(penalty = 0.1) |> 
    set_engine("keras")
  mr_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mr_cls_fit <- mr_cls_spec |> fit(island ~ ., data = penguins_train)
  mr_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mr_cls_fit, penguins_test),
    predict(mr_cls_fit, penguins_test, type = "prob")
  )
  ```

  </details>


  <details id="multinom-reg-nnet"> 

  <summary>With the `"nnet"` engine</summary>

  <h3>Classification Example (`nnet`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-multi-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mr_cls_spec <- 
    multinom_reg(penalty = 0.1) |> 
    set_engine("nnet")
  mr_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mr_cls_fit <- mr_cls_spec |> fit(island ~ ., data = penguins_train)
  mr_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mr_cls_fit, penguins_test),
    predict(mr_cls_fit, penguins_test, type = "prob")
  )
  ```

  </details>


  <details id="multinom-reg-brulee"> 

  <summary>With the `"brulee"` engine</summary>

  <h3>Classification Example (`brulee`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-multi-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  mr_cls_spec <- 
    multinom_reg(penalty = 0.1) |> 
    set_engine("brulee")
  mr_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  mr_cls_fit <- mr_cls_spec |> fit(island ~ ., data = penguins_train)
  mr_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(mr_cls_fit, penguins_test),
    predict(mr_cls_fit, penguins_test, type = "prob")
  )
  ```

  </details>
  
  
## `nearest_neighbor()` models

  <details id="nearest-neighbor-kknn"> 

  <summary>With the `"kknn"` engine</summary>

  <h3>Regression Example (`kknn`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  knn_reg_spec <-
    nearest_neighbor(neighbors = 5, weight_func = "triangular") |>
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |>
    set_engine("kknn")
  knn_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  knn_reg_fit <- knn_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  knn_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(knn_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`kknn`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  Since there are two classes, we'll use an odd number of neighbors to avoid ties:

  ```{r}
  knn_cls_spec <-
    nearest_neighbor(neighbors = 11, weight_func = "triangular") |>
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |>
    set_engine("kknn")
  knn_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  knn_cls_fit <- knn_cls_spec |> fit(Class ~ ., data = data_train)
  knn_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(knn_cls_fit, data_test),
    predict(knn_cls_fit, data_test, type = "prob")
  )
  ```
  
  </details>


## `rand_forest()` models

  <details id="rand-forest-ranger"> 
  
  <summary>With the `"ranger"` engine</summary>

  <h3>Regression Example (`ranger`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  rf_reg_spec <- 
    rand_forest(trees = 200, min_n = 5) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("ranger")
  rf_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  rf_reg_fit <- rf_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  rf_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(rf_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`ranger`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  rf_cls_spec <- 
    rand_forest(trees = 200, min_n = 5) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("ranger")
  rf_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  rf_cls_fit <- rf_cls_spec |> fit(Class ~ ., data = data_train)
  rf_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(rf_cls_fit, data_test),
    predict(rf_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


  <details id="rand-forest-randomForest"> 
  
  <summary>With the `"randomForest"` engine</summary>

  <h3>Regression Example (`randomForest`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  rf_reg_spec <- 
    rand_forest(trees = 200, min_n = 5) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("randomForest")
  rf_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  rf_reg_fit <- rf_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  rf_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(rf_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`randomForest`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  rf_cls_spec <- 
    rand_forest(trees = 200, min_n = 5) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("randomForest")
  rf_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  rf_cls_fit <- rf_cls_spec |> fit(Class ~ ., data = data_train)
  rf_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(rf_cls_fit, data_test),
    predict(rf_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


## `svm_linear()` models

  <details id="svm-linear-LiblineaR">
  
  <summary>With the `"LiblineaR"` engine</summary>

  <h3>Regression Example (`LiblineaR`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_reg_spec <- 
    svm_linear(cost = 1, margin = 0.1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("LiblineaR")
  svm_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_reg_fit <- svm_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  svm_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(svm_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`LiblineaR`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_cls_spec <- 
    svm_linear(cost = 1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("LiblineaR")
  svm_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_cls_fit <- svm_cls_spec |> fit(Class ~ ., data = data_train)
  svm_cls_fit
  ```

  The holdout data can be predicted for hard class predictions.

  ```{r}
  predict(svm_cls_fit, data_test)
  ```

  </details>


  <details id="svm-linear-kernlab"> 
  
  <summary>With the `"kernlab"` engine</summary>

  <h3>Regression Example (`kernlab`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_reg_spec <- 
    svm_linear(cost = 1, margin = 0.1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("kernlab")
  svm_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_reg_fit <- svm_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  svm_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(svm_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`kernlab`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_cls_spec <- 
    svm_linear(cost = 1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("kernlab")
  svm_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_cls_fit <- svm_cls_spec |> fit(Class ~ ., data = data_train)
  svm_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(svm_cls_fit, data_test),
    predict(svm_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


## `svm_poly()` models

  <details id="svm-poly-kernlab">
  
  <summary>With the `"kernlab"` engine</summary>

  <h3>Regression Example (`kernlab`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_reg_spec <- 
    svm_poly(cost = 1, margin = 0.1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("kernlab")
  svm_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_reg_fit <- svm_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  svm_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(svm_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`kernlab`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_cls_spec <- 
    svm_poly(cost = 1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("kernlab")
  svm_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_cls_fit <- svm_cls_spec |> fit(Class ~ ., data = data_train)
  svm_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(svm_cls_fit, data_test),
    predict(svm_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>


## `svm_rbf()` models

  <details id="svm-rbf-kernlab"> 

  <summary>With the `"kernlab"` engine</summary>

  <h3>Regression Example (`kernlab`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-reg-chicago.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_reg_spec <- 
    svm_rbf(cost = 1, margin = 0.1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("regression") |> 
    set_engine("kernlab")
  svm_reg_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_reg_fit <- svm_reg_spec |> fit(ridership ~ ., data = Chicago_train)
  svm_reg_fit
  ```

  The holdout data can be predicted:

  ```{r}
  predict(svm_reg_fit, Chicago_test)
  ```


  <h3>Classification Example (`kernlab`)</h3>

  ```{r}
  #| echo: false
  knitr::spin_child("template-cls-two-class.R")
  ```

  We can define the model with specific parameters:

  ```{r}
  svm_cls_spec <- 
    svm_rbf(cost = 1) |> 
    # This model can be used for classification or regression, so set mode
    set_mode("classification") |> 
    set_engine("kernlab")
  svm_cls_spec
  ```

  Now we create the model fit object:

  ```{r}
  set.seed(1)
  svm_cls_fit <- svm_cls_spec |> fit(Class ~ ., data = data_train)
  svm_cls_fit
  ```

  The holdout data can be predicted for both hard class predictions and probabilities. We'll bind these together into one tibble:

  ```{r}
  bind_cols(
    predict(svm_cls_fit, data_test),
    predict(svm_cls_fit, data_test, type = "prob")
  )
  ```
    
  </details>
