---
title: List of Models
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{List of Models}
output:
  knitr:::html_vignette:
    toc: yes
---

```{r ex_setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  digits = 3,
  collapse = TRUE,
  comment = "#>"
  )
options(digits = 3)
library(parsnip)
library(tidymodels)
library(cli)
library(kableExtra)
```

`parsnip` contains wrappers for a number of models. For example, the `parsnip` function `rand_forest()` can be used to create a random forest model. The **mode** of a model is related to its goal. Examples would be regression and classification. 

The list of models accessible via `parsnip` is:

```{r model-table, results = 'asis', echo = FALSE}
mod_names <- get_from_env("models")

mod_list <- 
  map_dfr(mod_names, ~ get_from_env(.x) %>% mutate(model = .x)) %>% 
  distinct(mode, model) %>% 
  mutate(model = paste0("`", model, "()`")) %>%
  arrange(mode, model) %>%
  group_by(mode) %>%
  summarize(models = paste(model, collapse = ", "))

for (i in 1:nrow(mod_list)) {
  cat(mod_list[["mode"]][i], ": ",
      mod_list[["models"]][i], "\n\n\n", 
      sep = "")
}
```

_How_ the model is created is related to the _engine_. In many cases, this is an R modeling package. In others, it may be a connection to an external system (such as Spark or Tensorflow). This table lists the engines for each model type along with the type of prediction that it can make (see `predict.model_fit()`). 

```{r pred-table, results = 'asis', echo = FALSE}
map_dfr(mod_names, ~ get_from_env(paste0(.x, "_predict")) %>% mutate(model = .x)) %>% 
  dplyr::select(-value) %>% 
  mutate(
    type = paste0("`", type, "`"),
    model = paste0("`", model, "()`"),
    ) %>%
  mutate(check = cli::symbol$tick) %>%
  spread(type, check, fill =  cli::symbol$times) %>%
  kable(format = "html") %>% 
  kable_styling(full_width = FALSE) %>%
  collapse_rows(columns = 1)
```

Models can be added by the user too. See the ["Making a `parsnip` model from scratch" vignette](Scratch.html).

