---
title: List of Models
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{List of Models}
output:
  knitr:::html_vignette:
    toc: yes
---

```{r ex_setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  digits = 3,
  collapse = TRUE,
  comment = "#>"
  )
options(digits = 3)
library(parsnip)
library(tidymodels)
library(cli)
library(kableExtra)
```

```{r modelinfo, inlcude = FALSE}
mod_names <- function(model, engine) {
  obj_name <- paste(model, engine, "data", sep = "_")
  tibble(module = getFromNamespace(obj_name, "parsnip") %>% names(),
         model = model, 
         engine = engine)
}

engine_info <- 
  parsnip:::engine_info %>%
  distinct(model, engine) %>% 
  mutate(obj_name = paste(model, engine, "data", sep = "_")) 
```

`parsnip` contains wrappers for a number of models. For example, the `parsnip` function `rand_forest()` can be used to create a random forest model. The **mode** of a model is related to its goal. Examples would be regression and classification. 

The list of models accessible via `parsnip` is:

```{r model-table, results = 'asis', echo = FALSE}
parsnip:::engine_info %>% 
  distinct(mode, model) %>% 
  mutate(model = paste0("`", model, "()`")) %>%
  arrange(mode, model) %>%
  as_tibble() %>%
  kable(format = "html") %>% 
  kable_styling(full_width = FALSE) %>%
  collapse_rows(columns = 1)
```

_How_ the model is created is related to the _engine_. In many cases, this is an R modeling package. In others, it may be a connection to an external system (such as Spark or Tensorflow). This table lists the engines for each model type along with the type of prediction that it can make (see `predict.model_fit()`). 

```{r pred-table, results = 'asis', echo = FALSE}
  map2_dfr(engine_info$model, engine_info$engine, mod_names) %>%
  dplyr::filter(!(module %in% c("libs", "fit"))) %>%
  mutate(
    module = ifelse(module == "pred", "num", module),
    module = ifelse(module == "confint", "conf_int", module),
    module = ifelse(module == "predint", "pred_int", module),   
    module = ifelse(module == "classes", "class", module),  
    module = paste0("`", module, "`"),
    model = paste0("`", model, "()`"),
    ) %>%
  mutate(check = cli::symbol$tick) %>%
  spread(module, check, fill =  cli::symbol$times) %>%
  kable(format = "html") %>% 
  kable_styling(full_width = FALSE) %>%
  collapse_rows(columns = 1)
```

Models can be added by the user too. See the "Making a `parsnip` model from scratch" vignette. 

